---
title: "Basic Plots 33 - Treemap Chart"
output: 
  html_document: 
    number_sections: yes
    toc: yes
    toc_depth: 4
    toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

First, you should load `recharts`:
```{r}
library(recharts)
```

# Introduction

Treemap chart includes 1 basic type:

- Treemap

<table id='intro'>
<tr><td>
```{r,echo=FALSE}
data <- data.frame(
    node=c('IOS', 'Android', 'Samsung', 'Apple', 'Huawei', 'Lenovo', 'Xiaomi', 
           'Others', 'LG', 'Oppo', 'Vivo', 'ZTE', 'Other'),
    parent=c(rep(NA, 2), 'Android', 'IOS', rep('Android', 4), rep('Others', 5)),
    series=(rep('Smartphone', 13)),
    value=c(231.5, 1201.4, 324.8, 231.5, 106.6, 74, 70.8, 625.2, 51.7, 49.1,
            42.6, 40, 243))
    
echartr(data, c(node, parent), value, facet=series, type='treemap') %>%
    setTitle('Smartphone Sales 2015 (M)','treemap', pos=5) %>% 
    setTheme('infographic', width=400, height=300)
```
</td>
<td>

</td></tr>
</table>

The keys are:

- character `x` with at least 2 columns: x[,1] are the nodes of the trees, x[,2] are parent nodes of the tree nodes. For root nodes, parent should be NA.
- numeric `y`
- `facet` is used to produce separate treemaps

# Function Call

```r
echartr(data, x, <y>, <series>, <facet>, <t>, <type>, <subtype>)
```

+--------+--------------------------------------------------------------------+
| Arg    |  Requirement                                                       |
+========+====================================================================+
|**data**| source data in the form of data.frame                            |
+--------+--------------------------------------------------------------------+
| **x**  | character independent variable. Each level of `x` is treated as a data series. Other type will be coerced to factors. Only the first two are accepted if multiple variables are provided: 1st one as nodes, 2nd one as parent nodes. |
+--------+--------------------------------------------------------------------+
| y      | numeric dependent variable. Only the first one is accepted if multiple variables are provided. |
+--------+--------------------------------------------------------------------+
| series | series variable which will be coerced to factors. Each level of `series` is treated as a grouping factor. Only the first one is accepted if multiple variables are provided. |
+--------+--------------------------------------------------------------------+
| facet  | facetting variable which will be coerced to factors. Each level of `facet` is treated as a subsetting factor to produce separate trees. Only the first one is accepted if multiple variables are provided. |
+--------+--------------------------------------------------------------------+
|  t     | timeline variable which will be coerced to factors. Only the first one is accepted if multiple variables are provided. |
+--------+--------------------------------------------------------------------+
| type   | 'treemap'. |
+--------+--------------------------------------------------------------------+

# Showcase

## Data Preparation

Let's prepare a data.frame to show the typical structure.

```{r}
data <- data.frame(
    node=c('IOS', 'Android', 'Samsung', 'Apple', 'Huawei', 'Lenovo', 'Xiaomi', 
           'Others', 'LG', 'Oppo', 'Vivo', 'ZTE', 'Other'),
    parent=c(rep(NA, 2), 'Android', 'IOS', rep('Android', 4), rep('Others', 5)),
    series=(rep('Smartphone', 13)),
    value=c(231.5, 1201.4, 324.8, 231.5, 106.6, 74, 70.8, 625.2, 51.7, 49.1,
            42.6, 40, 243))
knitr::kable(data)
```

The tree structure is defined by the mapping of nodes and parents.

- There are 1 series 'Smartphone', so we will see 1 treemap.
    - In the series 'Smartphone', we see 'IOS' and 'Android' have NA parent node. So 'IOS' and 'Android' will be the root nodes of this treemap.
        - Below the 'Android' root, we see 5 levels in parents nodes: 'Samsung', 'Huawei', 'Lenovo', 'Xiaomi' and 'Others'. So 'Android' node will contain 5 level-1 nodes.
            - There are 5 sub-nodes under 'Others'

You will see a breadcumb navigator under the treemap. The area of each tile is defined by `value`.

## Treemap Chart

### Single Treemap

`type` is set 'treemap'.

```{r}
echartr(data, c(node, parent), value, facet=series, type='treemap') %>%
    setTitle('Smartphone Sales 2015 (Million)', pos=5)
```

### Multiple Treemaps

You can modify the data a little bit to yield multiple `series`.

```{r}
data1 <- data[3:13,]
data1$series <- c('Android', 'IOS', rep('Android', 9))
data1$parent[1:6] <- NA
knitr::kable(data1)
```

Thus we get two treemaps.

```{r}
echartr(data1, c(node, parent), value, facet=series, type='treemap') %>%
    setTitle('Smartphone Sales 2015 (Million)', pos=5)
```


# Futher Setup

Then you can configure the widgets, add markLines and/or markPoints, fortify the chart.

You can refer to related functions to play around on your own.


