---
title: "Basic Plots 21 - WordCloud"
output: 
  html_document: 
    number_sections: yes
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

First, you should load `recharts`:
```{r}
library(recharts)
```

# Introduction

WordCloud has only 1 type: wordCloud

<table id='intro'>
<tr><td>
```{r,echo=FALSE}
getBaiduHot <- function(url, top=30, HTMLencoding='GB2312'){
    baiduhot <- paste0(readLines(url), collapse="")
    charset <- gsub('^.+charset=([[:alnum:]-]+?)[^[:alnum:]-].+$', "\\1", baiduhot)
    if (!is.null(charset)) HTMLencoding <- charset
    baiduhot <- iconv(baiduhot, from=HTMLencoding)
    hotword <- gsub(".+?<a class=\"list-title\"[^>]+?>([^<>]+?)</a>.+?<span class=\"icon-(rise|fair|fall)\">(\\d+?)</span>.+?","\\1\t\\3\t\\2\t", baiduhot)
    hotword <- enc2native(gsub("^(.+?)\t{4,}.+$","\\1",hotword))
    hotword <- t(matrix(unlist(strsplit(hotword,"\t")), nrow=3))
    hotword <- as.data.frame(hotword, stringsAsFactors=FALSE)
    names(hotword) <- c("Keyword", "Freq", "Trend")
    hotword$Freq <- as.numeric(hotword$Freq)
    hotword <- hotword[order(hotword$Freq, decreasing=TRUE),]
    return(hotword[1:top,])
}
hotword <- getBaiduHot("http://top.baidu.com/buzz?b=1")

echartr(hotword[1:30,], Keyword, Freq, type='wordCloud') %>% 
    setTheme('infographic', width=400, height=300)
```
</td>
<td>
</table>

The keys are:

- character `x` represents the words
- numeric `y` represents the frequency of the words
- `series` is not linked with legend, but linked with colors

# Function Call

```r
echartr(data, x, y, <z>, <type>)
```

+--------+--------------------------------------------------------------------+
| Arg    |  Requirement                                                       |
+========+====================================================================+
| **data** | source data in the form of data.frame                            |
+--------+--------------------------------------------------------------------+
| **x**  | character independent variable. Only the first one is accepted if multiple variables are provided. |
+--------+--------------------------------------------------------------------+
| **y**  | numeric dependent variable. Only the first one is accepted. |
+--------+--------------------------------------------------------------------+
| series | data series variable which will be coerced to factors. Only the first one is accepted if multiple variables are provided. |
+---------+--------------------------------------------------------------------+
|  z     | timeline variable which will be coerced to factors. Only the first one is accepted if multiple variables are provided. |
+--------+--------------------------------------------------------------------+
| type   | 'wordCloud' |
+--------+--------------------------------------------------------------------+


# Showcase

## Data Preparation

Fetch the Baidu buzz hotword web page and parse it into a data.frame Keyword and Freq.

For this purpose, we composed a function `getBaiduHot` to parse the _Baidu Hot Word Trend_ web page.

```{r}
getBaiduHot <- function(url, top=30, HTMLencoding='GB2312'){
    baiduhot <- paste0(readLines(url), collapse="")
    charset <- gsub('^.+charset=([[:alnum:]-]+?)[^[:alnum:]-].+$', "\\1", 
                    baiduhot)
    if (!is.null(charset)) HTMLencoding <- charset
    baiduhot <- iconv(baiduhot, from=HTMLencoding)
    hotword <- gsub(".+?<a class=\"list-title\"[^>]+?>([^<>]+?)</a>.+?<span class=\"icon-(rise|fair|fall)\">(\\d+?)</span>.+?","\\1\t\\3\t\\2\t", baiduhot)
    hotword <- enc2native(gsub("^(.+?)\t{4,}.+$","\\1", hotword))
    hotword <- t(matrix(unlist(strsplit(hotword,"\t")), nrow=3))
    hotword <- as.data.frame(hotword, stringsAsFactors=FALSE)
    names(hotword) <- c("Keyword", "Freq", "Trend")
    hotword$Freq <- as.numeric(hotword$Freq)
    hotword <- hotword[order(hotword$Freq, decreasing=TRUE),]
    return(hotword[1:top,])
}
hotword <- getBaiduHot("http://top.baidu.com/buzz?b=1")
knitr::kable(hotword)
```

## Basic Plot

Only provide `x` and `y`.

```{r}
echartr(hotword, Keyword, Freq, type='wordCloud') %>% 
    setTitle('Baidu Hot Word Top30 (realtime)', as.character(Sys.time()))
```

## Color by Series

We want to group the hot words. Let's assign a `series` variable 'Trend'. The 'rise' series and 'fall' series are colored differently.

```{r}
echartr(hotword, Keyword, Freq, Trend, type='wordCloud') %>% 
    setTitle('Baidu Hot Word Top30 (realtime)', as.character(Sys.time()))
```

## With Timeline

Let's compare realtime, today, and 7-days hotwords.

First, get the other two web pages and rbind the datasets.

```{r}
hotword$z <- 'Realtime'
hotword1 <- getBaiduHot("http://top.baidu.com/buzz?b=341&fr=topbuzz_b1")
hotword1$z <- 'Today'
hotword2 <- getBaiduHot("http://top.baidu.com/buzz?b=42&c=513&fr=topbuzz_b341")
hotword2$z <- '7-days'
hotword <- do.call('rbind', list(hotword, hotword1, hotword2))
hotword$z <- factor(hotword$z, levels=c('Realtime', 'Today', '7-days'))
```

Then come up with the chart.

```{r}
g <- echartr(hotword, Keyword, Freq, z=z, type='wordCloud') %>% 
    setTitle('Baidu Hot Word Top30')
g
```

# Futher Setup

Then you can configure the widgets, add markLines and/or markPoints, fortify the chart.

## `setTheme`

```{r}
g %>% setTheme('dark', palette='manyeyes')
```

You can refer to related functions to play around on your own.

