---
title: "Basic Plots 23 - Radar Chart"
output: 
  html_document: 
    number_sections: yes
    toc: yes
    toc_depth: 4
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

First, you should load `recharts`:
```{r}
library(recharts)
```

# Introduction

Radar plot includes 1 basic types:

- Radar

<table id='intro'>
<tr><td>
```{r,echo=FALSE}
cars = mtcars[c('Merc 450SE','Merc 450SL','Merc 450SLC'),
              c('mpg','disp','hp','qsec','wt','drat')]
cars$model <- rownames(cars)
cars <- data.table::melt(cars, id.vars='model')
names(cars) <- c('model', 'indicator', 'Parameter')
echartr(cars, indicator, Parameter, model, type='radar') %>%
        setTitle('Merc 450SE  vs  450SL  vs  450SLC') %>% 
    setTheme('infographic', width=400, height=300)
```
</td>
<td>

</td></tr>
</table>

The keys are:

- character `x` and numeric `y` and will be compacted using `data.table::dcast` with `fun=sum`
- **`x` is used as series, while `series` is used to produce separate pies!**
- you can use `setPolar` to tune the polar system parameters.

# Function Call

```r
echartr(data, x, <y>, <series>, <z>, <type>, <subtype>)
```

+--------+--------------------------------------------------------------------+
| Arg    |  Requirement                                                       |
+========+====================================================================+
|**data**| source data in the form of data.frame                            |
+--------+--------------------------------------------------------------------+
| **x**  | character independent variable. Each level of `x[,1]` is treated as polar axis labels, and `x[,2]` is treated as data series. Other type will be coerced to factors. Only the first two are accepted if multiple variables are provided. |
+--------+--------------------------------------------------------------------+
| **y**  | numeric dependent variable. Only the first one is accepted if multiple variables are provided. |
+--------+--------------------------------------------------------------------+
| series | series variable which will be coerced to factors. Each level of `series` is treated as a subsetting factor to produce separate pies. Only the first one is accepted if multiple variables are provided. |
+--------+--------------------------------------------------------------------+
|  z     | timeline variable which will be coerced to factors. Only the first one is accepted if multiple variables are provided. |
+--------+--------------------------------------------------------------------+
| type   | 'radar'. |
+--------+--------------------------------------------------------------------+
| subtype| - radar: "fill" | 
|        |     + fill: fill the radar with color (default hollow) |
+--------+--------------------------------------------------------------------+

# Showcase

## Data Preparation

Let's look into `mtcars` dataset embeded in the package `datasets`. We want to compare some paramters (c('mpg','disp','hp','qsec','wt','drat')) among several models (Mercedes-benz 450 series).

```{r}
cars = mtcars[c('Merc 450SE','Merc 450SL','Merc 450SLC'),
              c('mpg','disp','hp','qsec','wt','drat')]
cars$model <- rownames(cars)
cars <- data.table::melt(cars, id.vars='model')
names(cars) <- c('model', 'indicator', 'Parameter')
knitr::kable(cars)
```

## Radar Chart

### Single Radar

Set `type` 'radar' and do not set `series` or `x[,2]`. But such a radar chart makes little sense.

```{r}
echartr(cars, indicator, Parameter, type='radar')
```

### Radar with Multiple Series

So we always want to set data series to compare the parameters series by series. Radar chart is under polar coordinate system, so the data series is `x[,2]`

```{r}
echartr(cars, c(indicator, model), Parameter, type='radar', sub='fill') %>%
    setTitle('Merc 450SE  vs  450SL  vs  450SLC')
```

## Multiple Radars

If you don't set `x[,2]`, instead, set `series`, you will yield a bunch of radars shoulder by shoulder.

```{r}
echartr(cars, indicator, Parameter, model, type='radar') %>%
        setTitle('Merc 450SE  vs  450SL  vs  450SLC')
```


## With Timeline

You can set `z` to yield a radar chart with timeline.

```{r}
echartr(cars, indicator, Parameter, z=model, type='radar') %>%
        setTitle('Merc 450SE  vs  450SL  vs  450SLC')
```

When it comes to timeline, you should pay special attention. In order to make timeline work properly, you need an expand.grid dataset to cover all the combinations of x, series and `z` levels.

```{r}
carstat = data.table::dcast(data.table::data.table(mtcars),
              am + carb + gear ~., mean,
              value.var=c('mpg','disp','hp','qsec','wt','drat'))
carstat = data.table::melt(carstat, id=c('am', 'carb', 'gear'))
names(carstat) <- c('am', 'carb', 'gear', 'indicator', 'Parameter')
levels(carstat$indicator) <- gsub("_mean_\\.", "",
                                  levels(carstat$indicator))
carstat$am <- factor(carstat$am, labels=c('A', 'M'))
fullData <- data.frame(expand.grid(levels(carstat$indicator),
            levels(carstat$am), unique(carstat$carb)))
carstat <- merge(fullData, carstat, all.x=TRUE)
carstat$carb <- as.factor(carstat$carb)
carstat$gear <- as.factor(carstat$gear)
str(carstat)
```

```{r}
echartr(carstat, c(indicator, am), Parameter, carb, z=gear, type='radar') %>%
    setTitle('Merc 450SE  vs  450SL  vs  450SLC')
```

# Futher Setup

## `setPolar`

The default radar chart is built on polygons. You can built it on circle using `setPolar`, which is only appliable for radar charts.

```{r}
echartr(cars, indicator, Parameter, model, type='radar') %>%
        setTitle('Merc 450SE  vs  450SL  vs  450SLC') %>%
    setPolar(type='circle')
```

You can explore `setPolar` by typing `?setPolar` in R console.

Then you can configure the widgets, add markLines and/or markPoints, fortify the chart.

You can refer to related functions to play around on your own.

