---
title: "Basic Plots 05 - eventRiver"
output: 
  html_document: 
    number_sections: yes
    toc: yes
    toc_depth: 4
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

First, you should load `recharts`:
```{r}
library(recharts)
```

# Introduction

EventRiver plot contains 1 basic type: eventRiver.

<table id='intro'>
<tr><td>
```{r,echo=FALSE}
data(events)
events$link <- 'www.baidu.com'
events$img <- 'inst/favicon.png'
events$title <- paste(rownames(events), events$event)
echartr(events, c(time, event, title, link, img), c(value, weight), series, 
        type='eventRiver') %>% 
    setTheme('infographic', width=400, height=300) %>% 
    setTitle('Event River', 'Ficticious Data') %>% setXAxis('Time')
```
</td>
<td>
</table>

The keys are:

- `x` must be made of :
    - 2 compulsory columns: event slice time, events name
    - 3 optional columns: event slice title, event slice links, event slice images.
- `y` must be made of:
    - 1 compulsory column: slice value
    - 1 optional column: slice weight (default 1)
- `series` must be made of:
    - 2 optional columns: series, series weight (default 1)
- The variables must be provided following the exact order above.

# Function Call

```r
echartr(data, x, y, <z>, <series>, <type>)
```

+--------+--------------------------------------------------------------------+
| Arg    |  Requirement                                                       |
+========+====================================================================+
| **data** | source data in the form of data.frame                            |
+--------+--------------------------------------------------------------------+
| **x**  | character independent variable. It must contain 2 compulsory columns (event slice time, events name) and/or 3 optional columns (event slice title, event slice links, event slice images). The params list must exactly follow this order. |
+--------+--------------------------------------------------------------------+
| **y**  | numeric dependent variable. It must contain 1 compulsory column (slice value) and/or 1 optional column (slice weight). The params list must exactly follow this order. |
+--------+--------------------------------------------------------------------+
|  z     | timeline variable which will be coerced to factors. Only the first one is accepted if multiple variables are provided. |
+--------+--------------------------------------------------------------------+
| series | data series variable processed as factors. It contains 2 optional columns (series, series weight). The params list must exactly follow this order. |
+--------+--------------------------------------------------------------------+
| type   | 'eventRiver' |
+--------+--------------------------------------------------------------------+


# Showcase

## Basic Plot

```{r}
data(events)
events$link <- 'www.baidu.com'
events$img <- 'inst/favicon.png'
events$title <- paste(rownames(events), events$event)
echartr(events, c(time, event, title, link, img), c(value, weight), series, 
        type='eventRiver') %>% 
    setTitle('Event River', 'Ficticious Data') %>% setXAxis(name='Time') %>%
    setGrid(y2=80)
```

If you provide more details about each event slice (title, link and image) in `x`, the chart will be more informative.

# Futher Setup

Then you can configure the widgets, add markLines and/or markPoints, fortify the chart.

You can refer to related functions to play around on your own.

