---
title: "Basic Plots 14 - Force Chart"
output: 
  html_document: 
    number_sections: yes
    toc: yes
    toc_depth: 4
    toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

First, you should load `recharts`:
```{r}
library(recharts)
```

# Introduction

Force plot includes 2 basic types:

- Force chart with curve
- Force chart with line

<table id='intro'>
<tr><td>
```{r,echo=FALSE}
nodes <- cbind(yuNetwork$nodes[,1], NA, yuNetwork$nodes[,2:3],
               stringsAsFactors=FALSE)
names(nodes) <- names(yuNetwork$links)
yu <- rbind(yuNetwork$links, nodes, stringsAsFactors=FALSE)

echartr(yu, c(source, target), weight, relation, type='force') %>% 
    setTitle("Yu Family of Shaoxing") %>% setTheme(palette=c(
        'tan3','green3','green2','lawngreen','olivedrab1'), 
        width=400, height=300)
```
</td>
<td>
```{r,echo=FALSE}
echartr(yu, c(source, target), weight, relation, type='force_line') %>% 
    setTitle("Yu Family of Shaoxing") %>% setTheme(palette=c(
        'tan3','green3','green2','lawngreen','olivedrab1'), 
        width=400, height=300)
```
</td></tr>
</table>

The keys are:

- data structure:
  - matrix mode: A data.frame comprising of a column of name, and a numeric matrix. Assign the name column to x, the matrix to y.
  - node/link mode: node data.frame [x, NA, series, weight]; link data.frame [x, x1, relation, value]. Combine them using `rbind`. If you don't provide node data.frame, recharts will build it automatically. Assign the param list [x, x1, series/relation, weight/value] accordingly.
- force chart and chord chart are exchangeble by the toolbox buttons.

# Function Call

```r
echartr(data, x, <y>, <series>, <t>, <type>, <subtype>)
```

+--------+--------------------------------------------------------------------+
| Arg    |  Requirement                                                       |
+========+====================================================================+
|**data**| source data in the form of data.frame |
+--------+--------------------------------------------------------------------+
| **x**  | character independent variable. Other type will be coerced to factors. For node/link mode, you must provide two columns of `x`. For matrix mode, only the first column of `x` is accepted. |
+--------+--------------------------------------------------------------------+
| **y**  | numeric dependent variable. For node/link mode, only the first column of `y` is accepted. For matrix mode, all the columns of `y` are accepted. |
+--------+--------------------------------------------------------------------+
| series | series variable which will be coerced to factors. Only the first one is accepted if multiple variables are provided. |
+--------+--------------------------------------------------------------------+
|  t     | timeline variable which will be coerced to factors. Only the first one is accepted if multiple variables are provided. |
+--------+--------------------------------------------------------------------+
| type   | 'force'/'force_curve', 'force_line'. |
+--------+--------------------------------------------------------------------+
| subtype| - force: c("arrow", "triangle") | 
|        |     + arrow: The end symbol of the connection lines is arrow. |
|        |     + triangle: The end symbol of the connection lines is triangle |
|        | - force_line: c("arrow", "triangle")  |
+--------+--------------------------------------------------------------------+

# Showcase

## Data Preparation


### Matrix Mode

```{r}
grpmtx <- matrix(c(11975, 5871, 8916, 2868, 1951, 10048, 2060, 6171, 8010, 16145,
                   8090, 8045, 1013, 990, 940, 6907), byrow=TRUE, nrow=4)
grpmtx <- as.data.frame(grpmtx)
names(grpmtx) <- paste0('Group', 1:4)
grpmtx$Name <- paste0('Group', 1:4)
knitr::kable(grpmtx, align=c('lllll'))
```

The first 4 columns are exactly a matrix structure and the last column is a name vector. So this meets data structure requirements for matrix mode.

Matrix mode can be transformed to node/link mode as well. Matrix[i, j] represents 2 nodes (i & j) and 1 link (i -> j).

### Node/link Mode

```{r}
str(yuNetwork)
```

The yuNetwork dataset contains a nodes data.frame and a links data.frame. You can then combine them into one.

- nodes: 
    - `name`: the nodes name, 
    - `series`: the series that the nodes belongs to, 
    - `value`: the importance score of the nodes.
- links: 
    - `source` and `target`: defines the connections, 
    - `relation`: the name of the connections, 
    - `weight`: the importance sorce of the connections.

```{r}
nodes <- cbind(yuNetwork$nodes[,1], NA, yuNetwork$nodes[,2:3],
               stringsAsFactors=FALSE)
names(nodes) <- names(yuNetwork$links)
yu <- rbind(yuNetwork$links, nodes, stringsAsFactors=FALSE)
```


## Force Chart

### Force with Curve

Set `type` 'force'.

```{r}
echartr(yu, c(source, target), weight, relation, type='force') %>% 
    setTitle("Yu Family of Shaoxing") %>% setTheme(palette=c(
        'tan3','green3','green2','lawngreen','olivedrab1'))
```

### Force with Line

#### Matrix Mode

```{r}
echartr(grpmtx, Name, c(Group1, Group2, Group3, Group4), type='force_line') %>% 
  setTitle('Test Data', 'Force with ribbon')
```

#### Node/link Mode

Set `type` 'force_line'.

```{r}
echartr(yu, c(source, target), weight, relation, type='force_line') %>% 
    setTitle("Yu Family of Shaoxing") %>% setTheme(palette=c(
        'tan3','green3','green2','lawngreen','olivedrab1'))
```


### Force with Timeline

Let's use `year` columns as timeline.

```{r}
echartr(deutsch, c(club, player), weight, role, t=year,
        type='force', sub='arrow') %>% 
  setTitle('Club Orientation of Deutsch Soccer Team')
```

# Futher Setup

Then you can configure the widgets, add markLines and/or markPoints, fortify the chart.

You can refer to related functions to play around on your own.

