---
title: "Basic Plots 15 - Chord Chart"
output: 
  html_document: 
    number_sections: yes
    toc: yes
    toc_depth: 4
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

First, you should load `recharts`:
```{r}
library(recharts)
```

# Introduction

Chord plot includes 2 basic types:

- Chord with Ribbon
- Chord without Ribbon

<table id='intro'>
<tr><td>
```{r,echo=FALSE}
grpmtx <- matrix(c(11975, 5871, 8916, 2868, 1951, 10048, 2060, 6171, 8010, 16145,
                   8090, 8045, 1013, 990, 940, 6907), byrow=TRUE, nrow=4)
grpmtx <- as.data.frame(grpmtx)
names(grpmtx) <- paste0('Group', 1:4)
grpmtx$Name <- paste0('Group', 1:4)

echartr(grpmtx, Name, c(Group1, Group2, Group3, Group4), 
        type='chord', subtype='ribbon+asc+descsub+hidelab+scaletext') %>% 
  setTitle('Test Data','chord with ribbon') %>%
  setTheme('macarons', width=400, height=300)
```
</td>
<td>
```{r,echo=FALSE}
echartr(deutsch[deutsch$year==2014,], c(club, player), weight, role, type='chord', 
        sub='asc+descsub+rotatelab') %>% setTheme('infographic', width=400, height=300) %>% 
  setTitle('Club Orientation of Deutsch Soccer Team (2014)', 'Chord without ribbon')
```
</td></tr>
</table>

The keys are:

- data structure:
  - matrix mode: A data.frame comprising of a column of name, and a numeric matrix. Assign the name column to x, the matrix to y.
  - node/link mode: node data.frame [x, NA, series, weight]; link data.frame [x, x1, relation, value]. Combine them using `rbind`. If you don't provide node data.frame, recharts will build it automatically. Assign the param list [x, x1, series/relation, weight/value] accordingly.

# Function Call

```r
echartr(data, x, <y>, <series>, <t>, <type>, <subtype>)
```

+--------+--------------------------------------------------------------------+
| Arg    |  Requirement                                                       |
+========+====================================================================+
|**data**| source data in the form of data.frame |
+--------+--------------------------------------------------------------------+
| **x**  | character independent variable. Other type will be coerced to factors. For node/link mode, you must provide two columns of `x`. For matrix mode, only the first column of `x` is accepted. |
+--------+--------------------------------------------------------------------+
| **y**  | numeric dependent variable. For node/link mode, only the first column of `y` is accepted. For matrix mode, all the columns of `y` are accepted. |
+--------+--------------------------------------------------------------------+
| series | series variable which will be coerced to factors. Each level of `series` is treated as a subsetting factor to produce separate pies. Only the first one is accepted if multiple variables are provided. |
+--------+--------------------------------------------------------------------+
|  t     | timeline variable which will be coerced to factors. Only the first one is accepted if multiple variables are provided. |
+--------+--------------------------------------------------------------------+
| type   | 'chord'. |
+--------+--------------------------------------------------------------------+
| subtype| - chord: c("ribbon","scale","scaletext","rotatelab","hidelab","clock","clockwise","asc","desc","ascsub","descsub") | 
|        |     + ribbon: chort chart with ribbon. It requires dual-direction of links. |
|        |     + scale: Show scale on the ribbon. |
|        |     + scaletext: Show scale and text on the ribbon. |
|        |     + rotatelab: rotate the tick label. |
|        |     + hidelab: hide the label (default show). |
|        |     + clock/clockwise: ascending order is clockwise (default anti-clockwise). |
|        |     + asc: ascending nodes |
|        |     + desc:descending nodes  |
|        |     + ascsub: asceding chords |
|        |     + descsub: desceding chords |
+--------+--------------------------------------------------------------------+

# Showcase

## Data Preparation


### Matrix Mode

```{r}
grpmtx <- matrix(c(11975, 5871, 8916, 2868, 1951, 10048, 2060, 6171, 8010, 16145,
                   8090, 8045, 1013, 990, 940, 6907), byrow=TRUE, nrow=4)
grpmtx <- as.data.frame(grpmtx)
names(grpmtx) <- paste0('Group', 1:4)
grpmtx$Name <- paste0('Group', 1:4)
knitr::kable(grpmtx, align=c('lllll'))
```

The first 4 columns are exactly a matrix structure and the last column is a name vector. So this meets data structure requirements for matrix mode.

Matrix mode can be transformed to node/link mode as well. Matrix[i, j] represents 2 nodes (i & j) and 1 link (i -> j).

### Node/link Mode

```{r}
knitr::kable(deutsch[deutsch$year==2014,])
```

There is not a numeric matrix structure inside the data.frame, so it is node/link mode. There are no NAs in column 1 or 2, so in this case, `recharts` will build a node data.frame based on the data.frame given, which looks like:

```{r,echo=FALSE}
nodes <- data.frame(
  name=c(names(table(deutsch$player)), names(table((deutsch$club)))), 
  value=c(table(deutsch$player), table(deutsch$club)), series='')
knitr::kable(nodes, row.names=FALSE)
```

## Chord Chart

### Chord with Ribbon

Set `type` 'chord' and `subtype` 'ribbon'.

```{r}
echartr(grpmtx, Name, c(Group1, Group2, Group3, Group4), 
        type='chord', subtype='ribbon + asc + descsub + hidelab + scaletext') %>% 
  setTitle('Test Data','From d3.js')
```

### Chord without Ribbon

#### One-direction Relationship

Set `type` 'chord'. If the data structure does not include dual-direction relationship, no matter whether you assign `subtype` 'ribbon', ribbon will not display properly.

```{r}
echartr(deutsch[deutsch$year==2014,], c(club, player), weight, role, type='chord', 
        sub='asc + descsub + rotatelab') %>% 
  setTitle('Club Orientation of Deutsch Soccer Team (2014)')
```

#### Dual-direction Relationship

If you do want to display a chord with ribbon, you have to revise the data with dual-diretion relationship. 

By now, `deutsch14` only has one-direction relationship, which means, it only defines Gotze->Bayern, but not Bayern->Gotze.

```{r}
knitr::kable(with(deutsch[deutsch$year==2014,], table(player, club)))
```

What we need to do is duplicate the source and target columns to build a matrix.

```{r}
deutsch14 <- deutsch[deutsch$year==2014,]
deutsch14 <- rbind(deutsch14, deutsch14)
deutsch14[14:26, c('player', 'club')] <- recharts:::exchange(
    deutsch14[14:26, 'player'], deutsch14[14:26, 'club'])
knitr::kable(with(deutsch14, table(player, club)))
```

In this way set `subtype` 'ribbon' and we get a chord with ribbon.

```{r}
echartr(deutsch14, c(club, player), weight, role, type='chord', 
        sub='asc + descsub + rotatelab + ribbon') %>% 
  setTitle('Club Orientation of Deutsch Soccer Team (2014)')
```

Another example is based on preinstalled dataset **mideast**.

```{r}
mideast <- as.data.frame(mideast, col.names=mideast[1,], stringsAsFactors=FALSE)
names(mideast) <- mideast[1,]
mideast <- mideast[2:16,]
me <- data.table::melt(mideast, id=NA)
me <- me[!is.na(me$value),]
me$series <- strsplit(me$value, '/')
me$value <- sapply(me$series, function(x) as.numeric(x[2]))
me$series <- sapply(me$series, function(x) x[1])
names(me) <- c('source', 'target', 'value', 'series')
str(me)
```

```{r}
echartr(me, c(source, target), value, series, type='chord', sub='ribbon')
```

### Chord with Timeline

Let's use `year` columns as timeline.
```{r}
echartr(deutsch, c(club, player), weight, role, t=year, type='chord', 
        sub='asc + descsub + rotatelab') %>% 
    setTimeline(show=FALSE, autoPlay=TRUE) %>%
    setTitle('Club Orientation of Deutsch Soccer Team')
```

# Futher Setup

Then you can configure the widgets, add markLines and/or markPoints, fortify the chart.

You can refer to related functions to play around on your own.

