---
title: "Widget 25 - DataRange"
output: 
  html_document: 
    number_sections: yes
    toc: yes
    toc_depth: 4
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

First, you should load `recharts`:
```{r}
library(recharts)
```

# Introduction

The default position of dataRange is 8 o'clock.

The recommended approach to use `setDataRange` is `chart %>% setDataRange(...)`.

# Function Call

```r
setDataRange(chart, show = TRUE, pos = 8, valueRange = NULL,
  splitNumber = 5, itemGap = 5, labels = NULL, calculable = FALSE,
  borderColor = "#ccc", borderWidth = 0, selectedMode = list(TRUE,
  "single", "multiple"), color = c("#1e90ff", "#f0ffff"), splitList = NULL,
  initialRange = NULL, ...)
```

+-------------+----------------------------------------------------------------+
|   Arg       |  Requirement                                                |
+=============+================================================================+
| **chart**   | Echarts object generated by `echartR` or `echart`.  |
+-------------+----------------------------------------------------------------+
| show        | logical. Show the dataRange control if TRUE. If you want to remove dataRange from the echarts object, set it NULL. |
+-------------+----------------------------------------------------------------+
| pos         | the clock-position of dataRange, default 8. Refer to vecPos. Or you can define the position vector c(x, y, orient) yourself. |
+-------------+----------------------------------------------------------------+
| valueRange  | The range of the dataRange bar in form of c(min, max). If NULL, echarts default will be used. |
+-------------+----------------------------------------------------------------+
| splitNumber | How many discrete sections will the dataRange bar be divided into. Default 5. Set it to 0 to set the bar continuous and calculable will be accordingly set TRUE. |
+-------------+----------------------------------------------------------------+
| itemGap     | The gap between itmes in pixels. Default 10px. |
+-------------+----------------------------------------------------------------+
| labels      | The labels to the ends the dataRange bar in form `c('high end', 'low end')`. Default NULL, the min, max values will be used. |
+-------------+----------------------------------------------------------------+
| calculable  | Logical. If echart calculable feature is open. Default FALSE. If set calculable TRUE, splitNumber will be set 0. |
+-------------+----------------------------------------------------------------+
| borderColor | The border color of the dataRange bar. Default '#333'. |
+-------------+----------------------------------------------------------------+
| borderWidth | The border width of the dataRange bar. Default 0px (not shown). |
+-------------+----------------------------------------------------------------+
| selectedMode| The mode of the dataRange bar, default TRUE. You can also set it 'single' or 'multiple'. |
+-------------+----------------------------------------------------------------+
| color       | The hex vector of colors used for dataRange bar. Default c("#1e90ff", "#f0ffff"). |
+-------------+----------------------------------------------------------------+
| splitList   | A list for user-defined value split in the form of `list(list(start=m`, `end=n, label=x,` `color=hex), ...)`. If a valid splitList is set, splitNumber will be disabled. |
+-------------+----------------------------------------------------------------+
|initialRange | Initial selected value range in the form of `list(start=m, end=n)`, of which `m` and `n` all refer to percentage. |
+-------------+----------------------------------------------------------------+
| ...         | Elipsis. |
+-------------+----------------------------------------------------------------+

# Showcase

In a scatter chart, only `weight` is mapped to dataRange. So let's prepare a bubble chart.

```{r}
g <- echartr(iris, Sepal.Width, Petal.Width, Species, Petal.Length,
             type='bubble') %>% setSymbols('circle')
g
```

Initially dataRange is not shown. Let's turn if on. Then you will find dataRange color palette overides the orignial palette of the chart.
```{r}
g %>% setDataRange(show=TRUE)
```

Relocate the dataRange.
```{r}
g %>% setDataRange(pos=9)
```

Modify the valueRange.
```{r}
g %>% setDataRange(valueRange=c(0,10))
```

Render a continuous dataRange bar.
```{r}
g %>% setDataRange(splitNumber=0)
```

Customize the format.
```{r}
g %>% setDataRange(borderColor='gray', borderWidth=2,bgColor='yellow', 
                   itemGap=20)
```

Customize the color of the controls.
```{r}
g %>% setDataRange(color=getColFromPal('rainbow'))
```

By default, the splitNumber is 5 and the scale is evenly splited. You can assign user-defined splitList to overide the defaults.
```{r}
splitList <-list(
    list(start=5.1, end=7, label='5.1 - 7.0', color='red'),
    list(start=4.35, end=5.1, label='4.35 - 5.1', color='yellow'),
    list(start=1.6, end=4.35, label='1.6 - 4.35', color='lime'),
    list(start=0, end=1.6, label='0.0 - 1.6', color='cyan')
    )
g %>% setDataRange(splitList=splitList)
```

Set the initialRange when the dataRange is continuous.
```{r}
g %>% setDataRange(initialRange=list(start=20, end=60), splitNumber=0)
```

# References

<http://echarts.baidu.com/echarts2/doc/option.html#title~dataRange>
