---
title: "Widget 27 - RoamController"
output: 
  html_document: 
    number_sections: yes
    toc: yes
    toc_depth: 4
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

First, you should load `recharts`:
```{r}
library(recharts)
```

# Introduction

roamController is only for maps. The default position of roamController is 2 o'clock. Since the map can move and scale by default, roamController is not quite useful.

The recommended approach to use `setRoam` is `chart %>% setRoam(...)`.

# Function Call

```r
setRoam(chart, show = TRUE, pos = 2, width = 80, height = 120,
  bgColor = "rgba(0,0,0,0)", borderColor = "#ccc", borderWidth = 0,
  fillerColor = "#fff", handleColor = "#6495ed", step = 15,
  mapTypeControl = NULL, ...)
```

+--------------+---------------------------------------------------------------+
|   Arg        |  Requirement                                                |
+==============+===============================================================+
| **chart**    | Echarts object generated by `echartR` or `echart`.  |
+--------------+---------------------------------------------------------------+
| show         | logical. Show the roamController control if TRUE. If you want to remove roamController from the echarts object, set it NULL. |
+--------------+---------------------------------------------------------------+
| pos          | Clock position of the roamController. Default 2. Refer to `vecPos`. Or you can define the position vector `c(x, y, orient)` yourself. But note that roamController is always vertical. |
+--------------+---------------------------------------------------------------+
| width        | The width of the roamController. Default 80px. |
+--------------+---------------------------------------------------------------+
| height       | The width of the roamController. Default 120px. |
+--------------+---------------------------------------------------------------+
| bgColor      | background color, default transparent ('rgba(0,0,0,0)'). |
+--------------+---------------------------------------------------------------+
| borderColor  | Border color, default '#ccc'. |
+--------------+---------------------------------------------------------------+
| borderWidth  | Border width, default 0px (not shown). |
+--------------+---------------------------------------------------------------+
| fillerColor  | Filler color, default '#fff'. |
+--------------+---------------------------------------------------------------+
| handleColor  | Handle color, default '#6495ed'. |
+--------------+---------------------------------------------------------------+
| step         | Movement in px per move. Default 15px. |
+--------------+---------------------------------------------------------------+
|mapTypeControl| Which map to be controlled by roamController. E.g,, `list(china=TRUE)`. Default NULL and setRoam will calculate automatically. |
+--------------+---------------------------------------------------------------+
| ...          | Elipsis. |
+--------------+---------------------------------------------------------------+

# Showcase

```{r}
g <- echartr(NULL, type='map_china')
g
```

Initially roamController is not shown. Let's turn if on.
```{r}
g %>% setRoam(show=TRUE)
```

Relocate the roamController.
```{r}
g %>% setRoam(pos=8)
```

Customize the format.
```{r}
g %>% setRoam(bgColor='darkgray', fillerColor='white', handleColor='black')
```

set mapTypeControl and it no longer takes effect on China map.
```{r}
g %>% setRoam(mapTypeControl=list(world=TRUE))
```

# References

<http://echarts.baidu.com/echarts2/doc/option.html#title~roamController>
