---
title: "Widget 26 - DataZoom"
output: 
  html_document: 
    number_sections: yes
    toc: yes
    toc_depth: 4
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

First, you should load `recharts`:
```{r}
library(recharts)
```

# Introduction

The default position of dataZoom is 6 o'clock.

The recommended approach to use `setDataZoom` is `chart %>% setDataZoom(...)`.

# Function Call

```r
setDataZoom(chart, show = TRUE, pos = 6, range = NULL, width = 30,
  fill = "rgba(144,197,237,0.2)", handle = "rgba(70,130,180,0.8)",
  bgColor = "rgba(0,0,0,0)", dataBgColor = "#eee", showDetail = TRUE,
  realtime = FALSE, zoomLock = FALSE, ...)
```

+-------------+----------------------------------------------------------------+
|   Arg       |  Requirement                                                |
+=============+================================================================+
| **chart**   | Echarts object generated by `echartR` or `echart`.  |
+-------------+----------------------------------------------------------------+
| show        | logical. Show the dataZoom control if TRUE. If you want to remove dataZoom from the echarts object, set it NULL. |
+-------------+----------------------------------------------------------------+
| pos         | Clock position of the dataZoom. Default 6. Refer to `vecPos`. Or you can define the position vector `c(x, y, orient)` yourself. |
+-------------+----------------------------------------------------------------+
| range       | A vector of `c(min, max)`. Cannot be out of the frame `c(0, 100)` |
+-------------+----------------------------------------------------------------+
| width       | The width of the dataZoom bar. Default 20px. |
+-------------+----------------------------------------------------------------+
| fill        | fillerColor of the dataZoom bar, in character 'rgba(red, green, blue, alpha)' format. Default `'rgba(144,197,237,0.2)'` ("#90C5ED33"). |
+-------------+----------------------------------------------------------------+
| handle      | handleColor of the dataZoom bar, in character 'rgba(red, green, blue, alpha)' format. Default `'rgba(70,130,180,0.8)'` ("#4682B4CC"). |
+-------------+----------------------------------------------------------------+
| bgColor     | background color, default transparent ('rgba(0,0,0,0)'). |
+-------------+----------------------------------------------------------------+
| dataBgColor | background color of the data thumbnail (1st series). Default '#eee'. |
+-------------+----------------------------------------------------------------+
| showDetail  | Logical, if show the details when zooming. Defaul TRUE. |
+-------------+----------------------------------------------------------------+
| realtime    | Logical, if realtime display the changes when zooming. Default FALSE. |
+-------------+----------------------------------------------------------------+
| zoomLock    | Logical, if the zoom range is locked. Deafult FALSE. |
+-------------+----------------------------------------------------------------+
| ...         | Elipsis. |
+-------------+----------------------------------------------------------------+

# Showcase

```{r}
g <- echartr(iris, Sepal.Width, Petal.Width, Species)
g
```

Initially dataZoom is not shown. Let's turn if on.
```{r}
g %>% setDataZoom(show=TRUE)
```

Relocate the dataZoom
```{r}
g %>% setDataZoom(pos=12)
```

Customize the format.
```{r}
g %>% setDataZoom(bgColor='yellow', dataBgColor='gold', fill='tan',
                  handle='maroon')
```

Set the initial range 20% - 60%.

```{r}
g %>% setDataZoom(range=c(20, 60))
```

# References

<http://echarts.baidu.com/echarts2/doc/option.html#title~dataZoom>
