---
title: "Widget 03 - Grid"
output: 
  html_document: 
    number_sections: yes
    toc: yes
    toc_depth: 4
    toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

First, you should load `recharts`:
```{r}
library(recharts)
```

# Introduction

`setGrid` is used to set the pane grid when the chart is based on Cartesian Coordinate System (but may also take effect in other charts). 

`setGrid` family has two types of functions: setting grid and relocating widgets. The key is four parameters: x, y, x2, y2. The point (x, y) is the upper-left point of the widget/pane, while the point (x2, y2) is the lower-right point of the widgt/pane.

As every call of recharts functions automatically resizes the widgets, you are recommanded to put `setGrid` at the end of a pipe chain call.

# Function Call

All the function names have two forms: small camel and lowercase_underscore (endorsed by Hadley Wickham). To be lazy, we also provide short forms as well (e.g., dz for dataZoom).

```r
setGrid(chart, x = 80, y = 60, x2 = 80, y2 = 60, width = NULL,
  height = NULL, bgColor = NULL, borderColor = NULL, borderWidth = 1,
  widget = c("pane", "timeline", "legend", "title", "dataZoom", "dataRange",
  "toolbox", "roamController"), ...)
set_grid(chart, x = 80, y = 60, x2 = 80, y2 = 60, width = NULL,
  height = NULL, bgColor = NULL, borderColor = NULL, borderWidth = 1,
  widget = c("pane", "timeline", "legend", "title", "dataZoom", "dataRange",
  "toolbox", "roamController"), ...)

relocTitle(chart, x = NULL, y = NULL, ...)
move_title(chart, x = NULL, y = NULL, ...)

relocLegend(chart, x = NULL, y = NULL, ...)
move_legend(chart, x = NULL, y = NULL, ...)

relocDataZoom(chart, x = NULL, y = NULL, ...)
move_datazoom(chart, x = NULL, y = NULL, ...)
move_dz(chart, x = NULL, y = NULL, ...)

relocDataRange(chart, x = NULL, y = NULL, ...)
move_datarange(chart, x = NULL, y = NULL, ...)
move_dr(chart, x = NULL, y = NULL, ...)

relocTimeline(chart, x = NULL, y = NULL, x2 = NULL, y2 = NULL, ...)
move_timeline(chart, x = NULL, y = NULL, x2 = NULL, y2 = NULL, ...)
move_tl(chart, x = NULL, y = NULL, x2 = NULL, y2 = NULL, ...)

relocToolbox(chart, x = NULL, y = NULL, ...)
move_toolbox(chart, x = NULL, y = NULL, ...)
move_tb(chart, x = NULL, y = NULL, ...)

relocRoam(chart, x = NULL, y = NULL, ...)
move_roam(chart, x = NULL, y = NULL, ...)
move_rc(chart, x = NULL, y = NULL, ...)
```

+-------------+----------------------------------------------------------------+
|   Arg       |  Requirement                                                |
+=============+================================================================+
| **chart**   | Echarts object generated by `echartR` or `echart`.  |
+-------------+----------------------------------------------------------------+
| x           | x coordinate of the left upper point of the plot area. Default 80px. |
+-------------+----------------------------------------------------------------+
| y           | y coordinate of the left upper point of the plot area. Default 60px. |
+-------------+----------------------------------------------------------------+
| x2          | x coordinate of the right lower point of the plot area. Default 80px. |
+-------------+----------------------------------------------------------------+
| y2          | y coordinate of the right lower point of the plot area. Default 60px. |
+-------------+----------------------------------------------------------------+
| width       | Width of the plot area. Default NULL (automatically configured). |
+-------------+----------------------------------------------------------------+
| height      | Height of the plot area. Default NULL (automatically configured). |
+-------------+----------------------------------------------------------------+
| bgColor     | background color of plot area. Default transparent ('rgba(0,0,0,0)'). |
+-------------+----------------------------------------------------------------+
| borderColor | border color of the plot area. Default '#ccc'. |
+-------------+----------------------------------------------------------------+
| borderWidth | border width of the plot area. Default 0px (not shown). |
+-------------+----------------------------------------------------------------+
| widget      | Widget name to set. Could be c('pane', 'timeline', 'legend', 'title', 'dataZoom', 'dataRange', 'toolbox', 'roamController'). |
|             |           |
|             | - **pane**: the area pane, takes in all the parameters |
|             | - **timeline**: timeline widget, only use x, y, x2, y2 |
|             | - **legend, title, dataZoom, dataRange, toolbox, roamController**: other widgets, only use x, y |
+-------------+----------------------------------------------------------------+
| ...         | Elipsis. |
+-------------+----------------------------------------------------------------+


# Showcase

## Data Preparation

Let's use `airquality` to generate an Echarts objects `g`: 

```{r}
library(data.table)
aq1 <- melt(airquality, id=c('Month', 'Day'), measure=c('Temp', 'Wind'), 
            variable='Param')
g <- echartr(aq1, Day, value, Param, t=Month, type='curve') %>% 
    setToolbox(pos=3) %>% setTitle('Temp & Wind') %>% setDataZoom() %>% 
    setDataRange()
g
```

## Modification

`width` and `height` in `setGrid` are different from those in `setTheme`. `setGrid` only takes effect in the pane.

```{r}
g %>% setGrid(width=300, height=200)
```

We want to enlarge the grid a little bit. So we need to relocate some of the widgets and finally change the grid using `setGrid`.

Then relocate the widgets accordingly. The easiest way to relocate the widget is using `pos` argument in `set[Widgets]` function.

```{r}
g1 <- g %>% setTitle(pos=12)
g1
```

Now we can push timeline and dataZoom down to the bottom. Since dataRange only supports x and y, what if we want to put it in the bottom and stick to y2? The Echarts object has already been assigned a randomized `elementId` as metadata. We can use a JavaScript expression `document.getElementById(<elementId>).offsetHeight` to refer to the canvas height in a dynamic manner. No matter how we resize the canvas window, the widget will be always at the correct position.

```{r}
g2 <- g1
g2$elementId <- "chart2"
g2 <- g2 %>% relocDataZoom(x=120, y=JS(paste0(
    "document.getElementById('", g2$elementId, "').offsetHeight-30")))
g2
```

`timeline` supports x2 and y2. So we can directly set its y2 25. Thus, we exchaned the position of timeline and dataZoom.

```{r}
g3 <- g2 %>% relocTimeline(y2=25, x=120, x2=50)
g3$elementId <- "chart3"
g3
```

Finally let's enlarge the pane grid.

```{r}
g4 <- g3 %>% setGrid(x=120, y=40, x2=50, y2=90)
g4$elementId <- "chart4"
g4
```

# References

<http://echarts.baidu.com/echarts2/doc/option.html#title~grid>
