---
title: "Basic Plots 15 - Heatmap"
author: "Yiying Wang"
date: "`r Sys.Date()`"
output: 
  knitr:::html_vignette:
    number_sections: yes
    theme: cosmo
    toc: yes
    self_contained: no
    lib_dir: libs
vignette: >
  %\VignetteIndexEntry{Basic Plots 15 - Heatmap}
  %\VignetteEngine{knitr::rmarkdown_notangle}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

First, you should load `rechartsX`:
```{r}
library(rechartsX)
```

# Introduction

Heatmap has 1 basic type: heatmap.

<table id='intro'>
<tr><td>
```{r,echo=FALSE}
data = rbind(
    data.frame(
        lng=100+rnorm(100,0, 1)*600, lat=150+rnorm(100,0, 1)*50, 
        y=abs(rnorm(100,0,1))),
    data.frame(
        lng=rnorm(200,0, 1)*1000, lat=rnorm(200,0, 1)*800, 
        y=abs(rnorm(200,0,1))),
    data.frame(lng=400+rnorm(20,0, 1)*300, lat=5+rnorm(20,0, 1)*10, 
               y=abs(rnorm(100,0,1))))

echartr(data,lng=lng,lat=lat,y=y,type='heatmap') %>% setTitle("Heatmap") %>%
    setTheme('infographic', width=400, height=300)
```
</td>
<td>
</table>

The keys are:

- No need of `x`
- numeric `y`, numeric `lat` and `lng`

# Function Call

```r
echartr(data, y, lng, lat, <series>, <t>, <type>)
```

+--------+--------------------------------------------------------------------+
| Arg    |  Requirement                                                       |
+========+====================================================================+
| **data** | source data in the form of data.frame                            |
+--------+--------------------------------------------------------------------+
| **y**  | numeric dependent variable. Only the first one is accepted. `y` represents the heat value which is between 0 and 1. If `y` is not within this range, `rechartsX` will normalize it.|
+--------+--------------------------------------------------------------------+
| series | series variable which will be coerced to factors. Only the first one is accepted if multiple variables are provided. |
+--------+--------------------------------------------------------------------+
|**lng** | longitude or x-coordinate. |
+--------+--------------------------------------------------------------------+
|**lat** | latitude or y-coordinate. |
+--------+--------------------------------------------------------------------+
|  t     | timeline variable which will be coerced to factors. Only the first one is accepted if multiple variables are provided. |
+--------+--------------------------------------------------------------------+
| type   | 'heatmap' |
+--------+--------------------------------------------------------------------+


# Showcase

## Data Preparation

Here is a fictious dataset.

```{r}
data = rbind(
    data.frame(
        lng=100+rnorm(100,0, 1)*600, lat=150+rnorm(100,0, 1)*50, 
        y=abs(rnorm(100,0,1))),
    data.frame(
        lng=rnorm(200,0, 1)*1000, lat=rnorm(200,0, 1)*800, 
        y=abs(rnorm(200,0,1))),
    data.frame(lng=400+rnorm(20,0, 1)*300, lat=5+rnorm(20,0, 1)*10, 
               y=abs(rnorm(100,0,1))))
str(data)
```

## Basic Plot

```{r}
echartr(data,lng=lng,lat=lat,y=y,type='heatmap') %>% 
    setTitle("Heatmap", "Fictious Data")
```

Heatmap is more useful in maps. You can refer to `addHeatmap` for help.

# Futher Setup

Then you can configure the widgets, add markLines and/or markPoints, fortify the chart.

You can refer to related functions to play around on your own.

