---
title: "aesStyle"
author: "Yiying Wang"
date: "`r Sys.Date()`"
output: 
  knitr:::html_vignette:
    number_sections: yes
    theme: cosmo
    toc: yes
    self_contained: no
    lib_dir: libs
vignette: >
  %\VignetteIndexEntry{aesStyle}
  %\VignetteEngine{knitr::rmarkdown_notangle}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

First, you should load `recharts`:
```{r}
library(recharts)
```

# Introduction

`aesStyle` is a big family to construct Echarts styling element objects. E.g., Echarts uses `itemStyle` heavily, and you can either use `itemStyle` function or directly build the itemStyle object by writing a list.

Inside an itemStyle list object, there are three types of elements:

- atomic features
    - 'color', 'borderColor', 'borderWidth', 'barBorderColor', 'barBorderRadius', 'barBorderWidth', which you can directly assign values

- object features
    - 'lineStyle', 'textStyle','areaStyle', 'chordStyle', 'nodeStyle', 'linkStyle', which you can yield by aesStyle function family

- mixed object features
    - 'label' and 'labelLine', which contains other object features, such as 'lineStyle', 'textStyle'


# Function Call

```r
aesStyle(element = c("text", "line", "area", "chord", "node", "link"), ...)

lineStyle(...)

textStyle(...)

areaStyle(...)

chordStyle(...)

nodeStyle(...)

linkStyle(...)

labelStyle(...)

labelLineStyle(...)

itemStyle(...)
```

+--------------+---------------------------------------------------------------+
|   Arg        |  Requirement                                                |
+==============+===============================================================+
| **chart**    | Echarts object generated by `echartR` or `echart`.  |
+--------------+---------------------------------------------------------------+
| element      | c("text", "line", "area", "chord", "node", "link"). |
+--------------+---------------------------------------------------------------+
| ...          | The params to form an aesthetic element. |
+--------------+---------------------------------------------------------------+

## Elipsis

### `itemStyle` (normal|emphasis)

Arg         | Instruction
------------|-----------------------------------------------------------
color |	color vector, 'rgba', hex color, or color names.
lineStyle	| for line, k charts and markLine, see `lineStyle`
textStyle	| see `textStyle`
areaStyle	| for stacked line chart and map, see `areaStyle`
chordStyle	| for chord chart, see `chordStyle`
nodeStyle	| for force chart, see `nodeStyle`
linkStyle	| for force chart, see `linkStyle`
borderColor	| color vector, 'rgba', hex color, or color names.
borderWidth	| for symbol, symbole, pie chart, map and markPoint, numeric
barBorderColor	| for symbol, symbole, pie chart, map and markPoint, numeric
barBorderRadius	| numeric vector length 1 or 4 (right-bottom-left-top), default 0
barBorderWidth	| numeric vector length 1 or 4 (right-bottom-left-top), default 00
label	| for line, bar, k, scatter, pie, map, force, funnel charts and markPoint, markLine, see `labelStyle`
labelLine	| for pie and funnel chart, see `labelLineStyle`

### `labelStyle`

+------------+-----------------------------------------------------------------+
| Arg        | Instruction |
+============+=================================================================+
| show	     | TRUE|FALSE, default TRUE |
+------------+-----------------------------------------------------------------+
| position   | - for pie, 'outer'/'inner'; 
|            | - for funnel, 'inner'/'left'/'right'; 
|            | - for line, bar, k, scatter, 'top'/'right'/'inside'/'left'/'bottom'; 
|            | - for bar, additionally 'insideLeft' / 'insideRight' / 'insideTop' / 'insideBottom' |
+------------+-----------------------------------------------------------------+
| rotate     | chord chart only. TRUE|FALSE, default FALSE |
+------------+-----------------------------------------------------------------+
| distance   | chord and pie chart only. numeric, default 10 |
+------------+-----------------------------------------------------------------+
| formatter  | see `setTooltip` |
+------------+-----------------------------------------------------------------+
| textStyle  | see `textStyle` |
+------------+-----------------------------------------------------------------+
| x          | treemap only, numeric |
+------------+-----------------------------------------------------------------+
| y          | treemap only, numeric |
+------------+-----------------------------------------------------------------+

### `labelLineStyle`

Arg         | Instruction
------------|-----------------------------------------------------------
show	| TRUE|FALSE, default TRUE
length	| numeric or 'auto', default 40
lineStyle	| see `lineStyle`

### `textStyle`

Arg         | Instruction
------------|-----------------------------------------------------------
color	| color vector, 'rgba', hex color, or color names.
decoration	| only for tooltip. string, default 'none'
align	| 'left' / 'right' / 'center'
baseline	| 'top' / 'bottom' / 'middle'
fontFamily	| valid font family name
fontSize	| numeric, default 12
fontStyle	| 'normal' / 'italic' / 'oblique', default 'normal'
fontWeight	| 'normal' / 'bold' / 'bolder' / 'lighter' or numeric, default 'normal'

### `lineStyle`

Arg         | Instruction
------------|-----------------------------------------------------------
color	| color vector, 'rgba', hex color, or color names.
type	| 'solid' / 'dotted' / 'dashed', for tree, additionally 'curve' / 'broken'. Default 'solid'
width	| numeric
shadowColor	| color vector, 'rgba', hex color, or color names.
shadowBlur	| numeric, default 5
shadowOffsetX	| numeric, default 3
shadowOffsetY	| numeric, default 3

### `areaStyle`

Arg         | Instruction
------------|-----------------------------------------------------------
color	| color vector, 'rgba', hex color, or color names.
type	| only 'default'

### `chordStyle`

Arg         | Instruction
------------|-----------------------------------------------------------
width	| numeric, default 1
color	| color vector, 'rgba', hex color, or color names.
borderWidth	| numeric, default 1
borderColor	| color vector, 'rgba', hex color, or color names.

### `nodeStyle`

Arg         | Instruction
------------|-----------------------------------------------------------
color	| color vector, 'rgba', hex color, or color names.
borderWidth	| numeric, default 1
borderColor	| color vector, 'rgba', hex color, or color names.

### `linkStyle`

Arg         | Instruction
------------|-----------------------------------------------------------
type	| 'curve'|'line'
color	| color vector, 'rgba', hex color, or color names. default '#5182ab'
width	| numeric, default 1

# Showcase

How to build an itemStyle object?

First, build the low-level style element object.

```r
styText <- textStyle(color='red', fontFamily='Arial')
styLine <- lineStyle(color='#fff', width=4, shadowBlur=5)
```

Then, build up higher-level style element objects.

```r
lab <- labelStyle(show=TRUE, position='inside', textStyle=styText)
```

Finally, consolidate an itemSytle object.

```r
itemStyle <- list(normal=itemStyle(lineStyle=styLine, label=lab),
                  emphasis=itemStyle(lineStyle=styLine, label=lab)
              )
```

# References

<http://echarts.baidu.com/echarts2/doc/doc.html#ItemStyle>
