---
title: "Low-level Function: setSeries"
author: "Yiying Wang"
date: "`r Sys.Date()`"
output: 
  knitr:::html_vignette:
    number_sections: yes
    theme: cosmo
    toc: yes
    self_contained: no
    lib_dir: libs
vignette: >
  %\VignetteIndexEntry{Misc 02 - Low-level Function: setSeries}
  %\VignetteEngine{knitr::rmarkdown_notangle}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

First, you should load `recharts`:
```{r}
library(recharts)
```

# Introduction

The basic framework to make an Echarts object is 
```
Step 1 echart => Step 2 set[Widgets] => Step 3 set[Aesthetics]. 
```

Step 1 makes the structure of the Echarts object, step 2 creates/modifies its widgets, and step 3 modifies the params of the widgets. But what if you want to modify the details inside the series list? – You may want setSeries.

`setSeries` is a bit low-level, compared to other `set[Widgets]` functions. It directly passes the param list on to an Echarts object and may lead to unexpected results. So you are suggested to get more familiar with Echarts structure before you decide to `setSeries`.

# Function Call

```r
setSeries(chart, series = NULL, timeslots = NULL, ...)
```

+----------+-------------------------------------------------------------------+
|   Arg    |  Requirement                                                    |
+==========+===================================================================+
|**chart** | Echarts object generated by `echartR` or `echart`.  |
+----------+-------------------------------------------------------------------+
| series   | series, could be the name or the index of the series. When the string is not in the existing series list, it will be treated as new. If set NULL, the function applies to all the series. |
+----------+-------------------------------------------------------------------+
|timeslots | vector of timeslots, either name or index of timeline variable `z`. If set NULL, the function applies to all the timeslots. |
+----------+-------------------------------------------------------------------+
| ...      | Elipsis, containing the params to pass to the echarts object for modification.  |
+----------+-------------------------------------------------------------------+

## Generic Features in Elipsis

+-----------------+------------------------------------------------------------+
|  Feature        |  Interpretation |
+=================+============================================================+
| `type`          |  chart type. 'line', 'bar', 'scatter', 'k', 'pie', 'radar', 'chord', 'force', 'map'... If NULL, the series will not display. |
+-----------------+------------------------------------------------------------+
| `name`          | name of the series.  |
+-----------------+------------------------------------------------------------+
| `tooltip`       | `setTooltip` |
+-----------------+------------------------------------------------------------+
| `data`          | the data part of `echartR` |
+-----------------+------------------------------------------------------------+
| `itemStyle`     | `itemStyle` |
+-----------------+------------------------------------------------------------+
| `markPoint`     | `addMarkPoint` |
+-----------------+------------------------------------------------------------+
| `markLine`      | `addMarkLine` |
+-----------------+------------------------------------------------------------+
| `clickable`     | whether the data graph is clickable, default TRUE. |
+-----------------+------------------------------------------------------------+
| `z`             | level-2 layer control, default 2. |
+-----------------+------------------------------------------------------------+
| `zlevel`        | level-1 layer control, default 0. |
+-----------------+------------------------------------------------------------+

## Chart-type-specific Features in Elipsis

### Line/Area

+-----------------+------------------------------------------------------------+
|  Feature        |  Interpretation |
+=================+============================================================+
|`stack`          | TRUE/FALSE |
+-----------------+------------------------------------------------------------+
|`xAxisIndex`     | 0/1, default 0 (main axis) |
+-----------------+------------------------------------------------------------+
|`yAxisIndex`     | 0/1, default 0 (main axis) |
+-----------------+------------------------------------------------------------+
|`symbol`         | `setSymbols` |
+-----------------+------------------------------------------------------------+
|`symbolSize`     | numeric or JS function |
+-----------------+------------------------------------------------------------+
|`symbolRotate`   | -180 ~ 180 |
+-----------------+------------------------------------------------------------+
|`showAllSymbol`  | TRUE/FALSE, default FALSE |
+-----------------+------------------------------------------------------------+
|`smooth`         | TRUE/FALSE, default FALSE |
+-----------------+------------------------------------------------------------+
|`dataFilter`     | only for line charts. 'nearest'/'min'/'max'/'average', default 'nearest'. |
+-----------------+------------------------------------------------------------+
|`legendHoverLink`| TRUE/FALSE, default TRUE. |
+-----------------+------------------------------------------------------------+

### Bar/Column/Histogram

+-----------------+------------------------------------------------------------+
|  Feature        |  Interpretation |
+=================+============================================================+
|`stack`          | TRUE/FALSE |
+-----------------+------------------------------------------------------------+
|`xAxisIndex`     | 0/1, default 0 (main axis) |
+-----------------+------------------------------------------------------------+
|`yAxisIndex`     | 0/1, default 0 (main axis) |
+-----------------+------------------------------------------------------------+
|`barGap`         | percent or numeric, default '30%'. |
+-----------------+------------------------------------------------------------+
|`barCategoryGap` | percent or numeric, default '20%'. |
+-----------------+------------------------------------------------------------+
|`barMinHeight`   | numeric, default 0. |
+-----------------+------------------------------------------------------------+
|`barWidth`       | numeric, default automatic. |
+-----------------+------------------------------------------------------------+
|`barMaxWidth`    | numeric, default automatic. |
+-----------------+------------------------------------------------------------+
|`legendHoverLink`| TRUE/FALSE, default TRUE. |
+-----------------+------------------------------------------------------------+

### Scatter/Bubble

+-----------------+------------------------------------------------------------+
|  Feature        |  Interpretation |
+=================+============================================================+
|`xAxisIndex`     | 0/1, default 0 (main axis) |
+-----------------+------------------------------------------------------------+
|`yAxisIndex`     | 0/1, default 0 (main axis) |
+-----------------+------------------------------------------------------------+
|`symbol`         | `setSymbols` |
+-----------------+------------------------------------------------------------+
|`symbolSize`     | numeric or JS function |
+-----------------+------------------------------------------------------------+
|`symbolRotate`   |  -180 ~ 180 |
+-----------------+------------------------------------------------------------+
|`large`          |  TRUE/FALSE, default FALSE. |
+-----------------+------------------------------------------------------------+
|`largeThreshold` | numeric, default 2000. |
+-----------------+------------------------------------------------------------+
|`legendHoverLink`|  TRUE/FALSE, default TRUE. |
+-----------------+------------------------------------------------------------+

### Pie/Ring/Rose

+-----------------+------------------------------------------------------------+
|  Feature        |  Interpretation |
+=================+============================================================+
|`legendHoverLink`|  TRUE/FALSE, default TRUE. |
+-----------------+------------------------------------------------------------+
|`center`         | percent or numeric, default c('50%', '50%') |
+-----------------+------------------------------------------------------------+
|`radius`         | percent or numeric, default c(0, '75%') |
+-----------------+------------------------------------------------------------+
|`startAngle`     |  numeric -360 ~ 360, default 90 for pie. |
+-----------------+------------------------------------------------------------+
|`minAngle`       |  numeric, default 0. |
+-----------------+------------------------------------------------------------+
|`clockWise`      |  TRUE/FALSE, default TRUE. |
+-----------------+------------------------------------------------------------+
|`roseType`       | 'radius'/'area'. |
+-----------------+------------------------------------------------------------+
|`selectedOffset` | numeric, default 10. |
+-----------------+------------------------------------------------------------+
|`selectedMode`   |  NULL/'single'/'multiple', default NULL. |
+-----------------+------------------------------------------------------------+

### Radar

+-----------------+------------------------------------------------------------+
|  Feature        |  Interpretation |
+=================+============================================================+
|`symbol`         |  `setSymbols` |
+-----------------+------------------------------------------------------------+
|`symbolSize`     |   numeric or JS function |
+-----------------+------------------------------------------------------------+
|`symbolRotate`   |   -180 ~ 180 |
+-----------------+------------------------------------------------------------+
|`legendHoverLink`|   TRUE/FALSE, default TRUE. |
+-----------------+------------------------------------------------------------+
|`polarIndex`     |  numeric. Index of the polar system to host the series. |
+-----------------+------------------------------------------------------------+

### Chord

+-----------------+------------------------------------------------------------+
|  Feature        |  Interpretation |
+=================+============================================================+
|`symbol`         |  `setSymbols` |
+-----------------+------------------------------------------------------------+
|`symbolSize`     |  numeric or `JS` function |
+-----------------+------------------------------------------------------------+
|`clockWise`      |  TRUE/FASLE, default FALSE. |
+-----------------+------------------------------------------------------------+
|`categories`     |  character vector |
+-----------------+------------------------------------------------------------+
|`links`          |  list of links |
+-----------------+------------------------------------------------------------+
|`matrix`         |  matrix data |
+-----------------+------------------------------------------------------------+
|`minRadius`      |  numeric, default 10. |
+-----------------+------------------------------------------------------------+
|`maxRadius`      |  numeric, default 20. |
+-----------------+------------------------------------------------------------+
|`ribbonType`     |  TRUE/FALSE, default TRUE. |
+-----------------+------------------------------------------------------------+
|`showScale`      |  TRUE/FALSE, default FALSE. |
+-----------------+------------------------------------------------------------+
|`showScaleText`  |  TRUE/FALSE, default FALSE |
+-----------------+------------------------------------------------------------+
|`padding`        |  numeric, default 2. |
+-----------------+------------------------------------------------------------+
|`sort`           | 'none'/'ascending'/'descending', default 'none'. |
+-----------------+------------------------------------------------------------+
|`sortSub`        | 'none'/'ascending'/'descending', default 'none'. |
+-----------------+------------------------------------------------------------+
|`nodes`          |  nodes list |
+-----------------+------------------------------------------------------------+

### Force

+-----------------+------------------------------------------------------------+
|  Feature        |  Interpretation |
+=================+============================================================+
| `symbol`        | `setSymbols` |
+-----------------+------------------------------------------------------------+
| `symbolSize`    | numeric or `JS` function. |
+-----------------+------------------------------------------------------------+
| `large`         | TRUE/FALSE, default FALSE. |
+-----------------+------------------------------------------------------------+
| `center`        | percent or numeric, default c('50%', '50%'). |
+-----------------+------------------------------------------------------------+
| `roam`          | TRUE/FALSE/'scale'/'move', default FALSE. |
+-----------------+------------------------------------------------------------+
| `categories`    | character vector |
+-----------------+------------------------------------------------------------+
| `links`         | links list |
+-----------------+------------------------------------------------------------+
| `matrix`        | data matrix |
+-----------------+------------------------------------------------------------+
| `size`          | percent or numeric, default '100%' |
+-----------------+------------------------------------------------------------+
| `minRadius`     | numeric, default 10. |
+-----------------+------------------------------------------------------------+
| `maxRadius`     | numeric, default 20. |
+-----------------+------------------------------------------------------------+
| `linkSymbol`    | vector of symbol characters, default c('none', 'arrow') |
+-----------------+------------------------------------------------------------+
| `linkSymbolSize`| numeric verctor, default c(10, 15) |
+-----------------+------------------------------------------------------------+
| `scaling`       | numeric, default 1 |
+-----------------+------------------------------------------------------------+
| `gravity`       | numeric, default 1 |
+-----------------+------------------------------------------------------------+
| `draggable`     | TRUE/FALSE, default TRUE |
+-----------------+------------------------------------------------------------+
| `useWorker`     | TRUE/FALSE, default FALSE |
+-----------------+------------------------------------------------------------+
| `steps`         | numeric, default 1 |
+-----------------+------------------------------------------------------------+
| `nodes`         | nodes list |
+-----------------+------------------------------------------------------------+


### Map

+---------------------+--------------------------------------------------------+
|  Feature            |  Interpretation |
+=====================+========================================================+
| `selectedMode`      |  NULL/'single'/'multiple', default NULL |
+---------------------+--------------------------------------------------------+
| `mapType`           |  'china'/'world', default 'china' |
+---------------------+--------------------------------------------------------+
| `hoverable`         |  TRUE/FALSE, default TRUE |
+---------------------+--------------------------------------------------------+
|`dataRangeHoverLink` |  TRUE/FALSE, default TRUE |
+---------------------+--------------------------------------------------------+
| `mapLocation`       |  `list(x=.., y=.., width=.., height=..)`, default `list(x='center', y='center')` |
+---------------------+--------------------------------------------------------+
|`mapValueCalculation`|  'sum'/'average', default 'sum' |
+---------------------+--------------------------------------------------------+
| `mapValuePrecision` |  integer, default 0 |
+---------------------+--------------------------------------------------------+
| `showLegendSymbol`  |  TRUE/FALSE, default TRUE |
+---------------------+--------------------------------------------------------+
| `roam`              |  TRUE/FALSE/'scale'/'move', default FALSE |
+---------------------+--------------------------------------------------------+
| `scaleLimit`        |  numeric `list(max=.., min=..)`, default NULL |
+---------------------+--------------------------------------------------------+
| `nameMap`           | `addNameMap` |
+---------------------+--------------------------------------------------------+
| `textFixed`         | list, e.g., `list(China=c(10, -10))`, default NULL |
+---------------------+--------------------------------------------------------+
| `geoCoord`          | `addGeoCoord` |
+---------------------+--------------------------------------------------------+
| `heatmap`           | `addHeatMap` |
+---------------------+--------------------------------------------------------+
 
### Gauge

+-----------------+------------------------------------------------------------+
|  Feature        |  Interpretation |
+=================+============================================================+
|`legendHoverLink`|  TRUE/FALSE, default TRUE. |
+-----------------+------------------------------------------------------------+
| `center`        | percent or numeric vector, default c('50%', '50%') |
+-----------------+------------------------------------------------------------+
| `radius`        | percent or numeric vector, default c(0, '75%') |
+-----------------+------------------------------------------------------------+
| `startAngle`    | numeric -360 ~ 360, default 225 |
+-----------------+------------------------------------------------------------+
| `endAngle`      | numeric -360 ~ 360, default -45 |
+-----------------+------------------------------------------------------------+
| `min`           | numeric, default 0 |
+-----------------+------------------------------------------------------------+
| `max`           |  numeric, default 100 |
+-----------------+------------------------------------------------------------+
| `splitNumber`   | numeric, default 10 |
+-----------------+------------------------------------------------------------+
| `axisLine`      |  list, default `list( show=TRUE, lineStyle=list(color``=list(list(0.2, '#228b22'), list(0.8, '#48b'),` `list(1, '#ff4500')), width=30))` | 
+-----------------+------------------------------------------------------------+
| `axisTick`      | list, default `list( show=TRUE, splitNumber=5, length=8,` `lineStyle=list( color='#eee', width=1, type='solid'))` |
+-----------------+------------------------------------------------------------+
| `axisLabel`     | list, default `list(show=TRUE, formatter=NULL,` `textStyle=list(color='auto'))` |
+-----------------+------------------------------------------------------------+
| `splitLine`     | list, default `list(show=TRUE, length=30,` `lineStyle=list( color='#eee', width=2, type='solid'))`|
+-----------------+------------------------------------------------------------+
| `pointer`       | list, default `list(length='80%', width=8, color='auto')` |
+-----------------+------------------------------------------------------------+
| `title`         | list, default `list(show=TRUE, offsetCenter=list(0, '40%')`, `textStyle=list(color='#333', fontSize=15))`
+-----------------+------------------------------------------------------------+
| `detail`        | list, default `list(show=TRUE, backgroundColor='rgba(0,0,0,0)'`, `borderWidth=0, borderColor='#ccc',`  `width=100, height=40,` `offsetCenter=list(0, '40%'), formatter=NULL`, `textStyle=list(color='auto', fontSize=30))` |
+-----------------+------------------------------------------------------------+

### Funnel

+-----------------+------------------------------------------------------------+
|  Feature        | Interpretation |
+=================+============================================================+
|`legendHoverLink`| TRUE/FALSE, default TRUE. |
+-----------------+------------------------------------------------------------+
| `sort`          | 'ascending'|'descending', default 'descending' |
+-----------------+------------------------------------------------------------+
| `min`           | numeric, default 0 |
+-----------------+------------------------------------------------------------+
| `max`           | numeric, default 100 |
+-----------------+------------------------------------------------------------+
| `x`             | numeric, default 80 |
+-----------------+------------------------------------------------------------+
| `y`             | numeric, default 60 |
+-----------------+------------------------------------------------------------+
| `x2`            | numeric, default 80 |
+-----------------+------------------------------------------------------------+
| `y2`            | numeric, default 60 |
+-----------------+------------------------------------------------------------+
| `width`         | percent or numeric, default NULL |
+-----------------+------------------------------------------------------------+
| `height`        | percent or numeric, default NULL |
+-----------------+------------------------------------------------------------+
| `funnelAlign`   | 'left'/'right'/'center', default 'center' |
+-----------------+------------------------------------------------------------+
| `minSize`       |  percent, default '0%' |
+-----------------+------------------------------------------------------------+
| `maxSize`       |  percent, default '100%' |
+-----------------+------------------------------------------------------------+
| `gap`           |  numeric, default 0 |
+-----------------+------------------------------------------------------------+

### eventRiver

+-----------------+------------------------------------------------------------+
|  Feature        |  Interpretation |
+=================+============================================================+
| `xAxisIndex`    | 0/1, default 0 (main axis) |
+-----------------+------------------------------------------------------------+
|`legendHoverLink`| TRUE/FALSE, default TRUE. |
+-----------------+------------------------------------------------------------+
| `weight`        | numeric, default 1 |
+-----------------+------------------------------------------------------------+


### Treemap

+-----------------+------------------------------------------------------------+
|  Feature        |  Interpretation |
+=================+============================================================+
| `center`        |  percent or numeric vector, default c('50%', '50%') |
+-----------------+------------------------------------------------------------+
| `size`          |  percent or numeric vector, default c('80%', '80%') |
+-----------------+------------------------------------------------------------+
| `root`          |  name of the root displayed currently |
+-----------------+------------------------------------------------------------+


### Tree

+-----------------+------------------------------------------------------------+
|  Feature        |  Interpretation |
+=================+============================================================+
| `symbol`        | `setSymbols` |
+-----------------+------------------------------------------------------------+
| `symbolSize`    | numeric or JS function. |
+-----------------+------------------------------------------------------------+
| `roam`          | TRUE/FALSE/'scale'/'move', default FALSE |
+-----------------+------------------------------------------------------------+
| `rootLocation`  |  list, could be `list(x='center' / 'left' / 'right' / 'x%' / number,` `y='center' / 'top' / 'bottom' / 'y%' / number)` |
+-----------------+------------------------------------------------------------+
| `layerPadding`  |  numeric, default 100 |
+-----------------+------------------------------------------------------------+
| `nodePadding`   |  numeric, default 30 |
+-----------------+------------------------------------------------------------+
| `orient`        | 'vertical'/'horizontal'/'radial', default 'vertical' |
+-----------------+------------------------------------------------------------+
| `direction`     |  "" or "inverse", default "" |
+-----------------+------------------------------------------------------------+

### wordCloud

+-----------------+------------------------------------------------------------+
|  Feature        |  Interpretation |
+=================+============================================================+
| `center`        |  percent or numeric vector, default c('50%', '50%') |
+-----------------+------------------------------------------------------------+
| `size`          |  percent or numeric vector, default c('80%', '80%') |
+-----------------+------------------------------------------------------------+
| `textRotation`  |  vector, -90 ~ 90, default c(0, 90) |
+-----------------+------------------------------------------------------------+
| `autoSize`      |  list, default `list(enable=TRUE, minSize=12)` |
+-----------------+------------------------------------------------------------+

### Heatmap

+-----------------+------------------------------------------------------------+
|  Feature        | Interpretation |
+=================+============================================================+
| `blurSize`      | numeric, default 30 |
+-----------------+------------------------------------------------------------+
| `gradientColors`| `list(offset=.., color=..)` or color vector. default `list('blue', 'cyan', 'limegreen', 'yellow', 'red')` |
+-----------------+------------------------------------------------------------+
| `minAlpha`      | numeric, default 0.05 |
+-----------------+------------------------------------------------------------+
| `valueScale`    | numeric, default 1 |
+-----------------+------------------------------------------------------------+
| `opacity`       | numeric, default 1 |
+-----------------+------------------------------------------------------------+
 
# Showcase

## Data Preparation

Let's use `airquality` to generate 4 Echarts objects `g1` - `g4`: 

**timeline**  | **mono series** | **multi series**
--------------|-----------------|-----------------
**no**        |  `g1`           |  `g2`
**yes**       |  `g3`           |  `g4`

```{r}
require(data.table)
aq <- airquality
aq$Date <- as.Date(paste('1973', aq$Month, aq$Day, sep='-'))
g1 <- echartr(aq, Date, Temp, type='curve') %>% setToolbox(pos=3)
g2 <- echartr(aq, Day, Temp, Month, type='curve') %>% setToolbox(pos=3)
g3 <- echartr(aq, Day, Temp, t=Month, type='curve') %>% setToolbox(pos=3)
aq1 <- melt(aq, id=c('Month', 'Day'), measure=c('Temp', 'Wind'), 
            variable='Param')
g4 <- echartr(aq1, Day, value, Param, t=Month, type='curve') %>% 
    setToolbox(pos=3)
```


## Modification

`setSeries` can modify everything within series.

You can change chart type and THEN tune the new graph features.

```r
g1 %>% setSeries(type='bar') %>% setSeries(barWidth=0.5)
```

<table>
<tr><td>
```{r, echo=FALSE}
g1 %>% setTheme(width=400, height=300)
```
</td><td>
```{r, echo=FALSE}
g1 %>% setSeries(type='bar') %>% setSeries(barWidth=0.5) %>% setTheme(width=400, height=300)
```
</td></tr>
</table>

You can limit the modification in some certain series...

```r
g2 %>% setSeries(series='5', itemStyle=list(normal=itemStyle(
    lineStyle=lineStyle(shadowBlur=10, shadowColor='yellow')))
```

<table>
<tr><td>
```{r,echo=FALSE}
g2 %>% setTheme(width=400, height=300)
```
</td><td>
```{r,echo=FALSE}
g2 %>% setSeries(series='5', itemStyle=list(normal=itemStyle(
    lineStyle=lineStyle(shadowBlur=10, shadowColor='yellow')))) %>% 
    setTheme(width=400, height=300)
```
</td></tr>
</table>


or timeslots... 

> But the features tend to inherit by timeslot, so you need to reset the features on the following timeslot to block the inheritibility.

```r
g3 %>% setSeries(timeslots='5', itemStyle=list(normal=itemStyle(
    lineStyle=lineStyle(shadowBlur=10, shadowColor='yellow')))) %>%
    setSeries(timeslots='6', itemStyle=list(normal=itemStyle(
    lineStyle=lineStyle(shadowBlur=0))))
```

<table>
<tr><td>
```{r,echo=FALSE}
g3 %>% setTheme(width=400, height=300)
```
</td><td>
```{r,echo=FALSE}
g3 %>% setSeries(timeslots='5', itemStyle=list(normal=itemStyle(
    lineStyle=lineStyle(shadowBlur=10, shadowColor='yellow')))) %>%
    setSeries(timeslots='6', itemStyle=list(normal=itemStyle(
    lineStyle=lineStyle(shadowBlur=0)))) %>% setTheme(width=400, height=300)
```
</td></tr>
</table>


or combination of series and timeslots. 

```r
g4 %>% setSeries(series='Temp', timeslots='5', itemStyle=list(normal=itemStyle(
    lineStyle=lineStyle(shadowBlur=10, shadowColor='yellow')))) %>%
    setSeries(timeslots='6', series='Temp', itemStyle=list(normal=itemStyle(
        lineStyle=lineStyle(shadowBlur=0)
    )))
```

<table>
<tr><td>
```{r,echo=FALSE}
g4 %>% setTheme(width=400, height=300)
```
</td><td>
```{r,echo=FALSE}
g4 %>% setSeries(series='Temp', timeslots='5', itemStyle=list(normal=itemStyle(
    lineStyle=lineStyle(shadowBlur=10, shadowColor='yellow')))) %>%
    setSeries(timeslots='6', series='Temp', itemStyle=list(normal=itemStyle(
        lineStyle=lineStyle(shadowBlur=0)
    ))) %>% setTheme(width=400, height=300)
```
</td></tr>
</table>

# References

<http://echarts.baidu.com/echarts2/doc/option.html#title~series-i>
