---
title: "Basic Plots 32 - Tree Chart"
author: "Yiying Wang"
date: "`r Sys.Date()`"
output: 
  knitr:::html_vignette:
    number_sections: yes
    theme: cosmo
    toc: yes
    self_contained: no
    lib_dir: libs
vignette: >
  %\VignetteIndexEntry{Basic Plots 32 - Tree Chart}
  %\VignetteEngine{knitr::rmarkdown_notangle}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

First, you should load `rechartsX`:
```{r}
library(rechartsX)
```

# Introduction

Tree chart includes 4 basic types:

- Horizontal tree
- Inverse horizontal tree
- Vertical tree
- Inverse vertical tree

<table id='intro'>
<tr><td>
```{r,echo=FALSE}
data <- data.frame(
    node=c('North America', 'USA', 'Canada', 'California', 'New York', 
           'Massachusetts', 'Quebec', 'Ontario', 'South America',
           'Brazil', 'Argentina', 'Rio de Jeneiro', 'Sao Paolo', 'Buenos Aires',
           'Mendosa'),
    parent=c(NA, rep('North America', 2), rep('USA', 3), rep('Canada', 2),
             NA, rep('South America', 2), rep('Brazil', 2), rep('Argentina', 2)),
    series=c(rep('Tree 1', 8), rep('Tree 2', 7)),
    value=rep(1, 15))
    
echartr(data, c(node, parent), value, facet=series, type='tree') %>%
    setTitle('tree') %>% setTheme('infographic', width=400, height=300)
```
</td>
<td>
```{r,echo=FALSE}
echartr(data, c(node, parent), value, facet=series, type='tree_inv') %>%
    setTitle('tree_inv') %>% setTheme('roma', width=400, height=300)
```
</td></tr>
<tr><td>
```{r,echo=FALSE}
echartr(data, c(node, parent), value, facet=series, type='htree') %>%
    setTitle('htree') %>% setTheme('macarons', width=400, height=300)
```
</td><td>
```{r,echo=FALSE}
echartr(data, c(node, parent), value, facet=series, type='htree_inv') %>%
    setTitle('htree_inv') %>% setTheme('macarons2', width=400, height=300)
```
</td></tr>
</table>

The keys are:

- character `x` with at least 2 columns: x[,1] are the nodes of the trees, x[,2] are parent nodes of the tree nodes. For root nodes, parent should be NA.
- numeric `y`
- `facet` is used to produce separate trees

# Function Call

```r
echartr(data, x, <y>, <series>, <facet>, <t>, <type>, <subtype>)
```

+--------+--------------------------------------------------------------------+
| Arg    |  Requirement                                                       |
+========+====================================================================+
|**data**| source data in the form of data.frame                            |
+--------+--------------------------------------------------------------------+
| **x**  | character independent variable. Each level of `x` is treated as a data series. Other type will be coerced to factors. Only the first two are accepted if multiple variables are provided: 1st one as nodes, 2nd one as parent nodes. |
+--------+--------------------------------------------------------------------+
| y      | numeric dependent variable. Only the first one is accepted if multiple variables are provided. |
+--------+--------------------------------------------------------------------+
| series | series variable which will be coerced to factors. Each level of `series` is treated as a grouping factor. Only the first one is accepted if multiple variables are provided. |
+--------+--------------------------------------------------------------------+
| facet  | facetting variable which will be coerced to factors. Each level of `facet` is treated as a subsetting factor to produce separate trees. Only the first one is accepted if multiple variables are provided. |
+--------+--------------------------------------------------------------------+
|  t     | timeline variable which will be coerced to factors. Only the first one is accepted if multiple variables are provided. |
+--------+--------------------------------------------------------------------+
| type   | 'tree'/'vtree', 'tree_inv'/'vtree_inv', 'htree', 'htree_inv'. |
+--------+--------------------------------------------------------------------+
| subtype| - tree: c("curve","broken","dotted","dashed","solid") | 
|        |     + curve: nodes are connected by curve |
|        |     + broken: nodes are connected by broken lines |
|        |     + dotted: the connection lines are dotted |
|        |     + solid: the connection lines are solid |
|        |     + dashed: the connection lines are dashed |
|        | - tree_inv: c("curve","broken","dotted","dashed","solid") |
|        | - htree: c("curve","broken","dotted","dashed","solid") |
|        | - htree_inv: c("curve","broken","dotted","dashed","solid") |
+--------+--------------------------------------------------------------------+


# Showcase

## Data Preparation

Let's prepare a data.frame to show the typical structure.

```{r}
data <- data.frame(
    node=c('North America', 'USA', 'Canada', 'California', 'New York', 
           'Massachusetts', 'Quebec', 'Ontario', 'South America',
           'Brazil', 'Argentina', 'Rio de Jeneiro', 'Sao Paolo', 'Buenos Aires',
           'Mendosa'),
    parent=c(NA, rep('North America', 2), rep('USA', 3), rep('Canada', 2),
             NA, rep('South America', 2), rep('Brazil', 2), rep('Argentina', 2)),
    series=c(rep('Tree 1', 8), rep('Tree 2', 7)),
    value=rep(1, 15))
knitr::kable(data)
```

The tree structure is defined by the mapping of nodes and parents.

- There are two series 'Tree 1' and 'Tree 2', so we will see two trees.
    - In the series 'Tree 1', we see 'North America' has NA parent node. So 'North America' will be the root node of this tree.
        - Below the root, we see 2 levels in parents nodes: 'USA' and 'Canada'. So 'Tree 1' tree will contain 2 level-1 nodes under the root 'North America'.
            - There are 3 nodes with 'USA' as parent: 'California', "New York" and "Massachusetts"
            - There are 2 nodes with 'Canada' as parent: 'Ontario' and 'Quebec'

## Tree Chart

### Single Tree

`type` is set 'tree'.

```{r}
echartr(data[data$series=='Tree 1',], c(node, parent), value, type='tree') %>%
    setTitle('Single Tree')
```

### Multiple Trees

If you assign `series` with a valid data structure, you yield multiple trees.
But Echarts does not map `series` with legend and color well. So you need to color the trees separately.

```{r}
echartr(data, c(node, parent), value, facet=series, type='tree') %>%
    setTitle('Multiple Trees')
```

## Inverse Tree Chart

Set `type` 'tree_inv'. Here you can test `subtype`s. 

```{r}
echartr(data, c(node, parent), value, facet=series, type='tree_inv',
        subtype='broken') %>% setTitle('tree_inv')
```

## Horizontal Tree

Set `type` 'htree'.

```{r}
echartr(data, c(node, parent), value, facet=series, type='htree', 
        subtype='broken + dashed') %>% setTitle('htree')
```

## Inverse Horzontal Tree

Set `type` 'htree_inv'.

```{r}
echartr(data, c(node, parent), value, facet=series, type='htree_inv', 
        subtype='broken + dotted') %>% setTitle('htree_inv')
```


# Futher Setup

Then you can configure the widgets, add markLines and/or markPoints, fortify the chart.

You can refer to related functions to play around on your own.


