---
title: "Basic Plots 24 - Gauge"
author: "Yiying Wang"
date: "`r Sys.Date()`"
output: 
  knitr:::html_vignette:
    number_sections: yes
    theme: cosmo
    toc: yes
    self_contained: no
    lib_dir: libs
vignette: >
  %\VignetteIndexEntry{Basic Plots 24 - Gauge}
  %\VignetteEngine{knitr::rmarkdown_notangle}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

First, you should load `recharts`:
```{r}
library(recharts)
```

# Introduction

Gauge is also known as dashboard.

<table id='intro'>
<tr><td>
```{r,echo=FALSE}
data = data.frame(x='kph', y=70)
echartr(data, x, y, type='gauge') %>% 
    setTheme('macarons', width=400, height=300) %>% 
    setTitle('KM per Hour')
```
</td>
<td>
</table>

The keys are:

- character `x` 
- numeric `y`
- character `facet` to yield multiple gauges
- `t` if you want the gauge change

# Function Call

```r
echartr(data, x, y, <series>, <facet>, <t>, <type>)
```

+--------+--------------------------------------------------------------------+
| Arg    |  Requirement                                                       |
+========+====================================================================+
| **data** | source data in the form of data.frame                            |
+--------+--------------------------------------------------------------------+
| **x**  | character independent variable. Only the first one is accepted if multiple variables are provided. |
+--------+--------------------------------------------------------------------+
| **y**  | numeric dependent variable. Only the first one is accepted. |
+--------+--------------------------------------------------------------------+
| series | series variable which will be coerced to factors. Each level of `series` is treated as a subsetting factor to produce. Only the first one is accepted if multiple variables are provided. |
+--------+--------------------------------------------------------------------+
| facet  | facetting variable which will be coerced to factors. Each level of `facet` is treated as a subsetting factor to produce separate gauges. Only the first one is accepted if multiple variables are provided. |
+--------+--------------------------------------------------------------------+
|  t     | timeline variable which will be coerced to factors. Only the first one is accepted if multiple variables are provided. |
+--------+--------------------------------------------------------------------+
| type   | 'gauge' |
+--------+--------------------------------------------------------------------+


# Showcase

## Data Preparation

Here is a fictious dataset.

```{r}
data = data.frame(x=rep(c('KR/min', 'Kph'), 2), y=c(6.3, 54, 7.5, 82), 
                  z=c(rep('t1', 2), rep('t2', 2)))
knitr::kable(data)
```

## Single Gauge

```{r}
echartr(data, x, y, type='gauge')
```

## Multiple Gauges

```{r}
echartr(data, x, y, facet=x, type='gauge')
```

## With Timeline


```{r}
echartr(data, x, y, facet=x, t=z, type='gauge')
```

# Futher Setup

Then you can configure the widgets, add markLines and/or markPoints, fortify the chart.

You can refer to related functions to play around on your own.

