---
title: "Basic Plots 14 - Venn"
author: "Yiying Wang"
date: "`r Sys.Date()`"
output: 
  knitr:::html_vignette:
    number_sections: yes
    theme: cosmo
    toc: yes
    self_contained: no
    lib_dir: libs
vignette: >
  %\VignetteIndexEntry{Basic Plots 14 - Venn}
  %\VignetteEngine{knitr::rmarkdown_notangle}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

First, you should load `rechartsX`:
```{r}
library(rechartsX)
```

# Introduction

Venn has very limited functionalities in Echarts.

<table id='intro'>
<tr><td>
```{r,echo=FALSE}
data = data.frame(x=c('Collection 1', 'Collection 2', 'Intersection'), 
                  y=c(40,50,20))
echartr(data, x, y, type='venn') %>% 
    setTheme('macarons', width=400, height=300) %>% 
    setTitle('Venn')
```
</td>
<td>
</table>

The keys are:

- character `x` and numeric `y` 
- 3 rows with which the last row is the intersect
- `series` is not applicable

# Function Call

```r
echartr(data, x, y, <t>, <type>)
```

+--------+--------------------------------------------------------------------+
| Arg    |  Requirement                                                       |
+========+====================================================================+
| **data** | source data in the form of data.frame                            |
+--------+--------------------------------------------------------------------+
| **x**  | character independent variable. Only the first one is accepted if multiple variables are provided. |
+--------+--------------------------------------------------------------------+
| **y**  | numeric dependent variable. Only the first four ones are accepted. |
+--------+--------------------------------------------------------------------+
|  t     | timeline variable which will be coerced to factors. Only the first one is accepted if multiple variables are provided. |
+--------+--------------------------------------------------------------------+
| type   | 'venn' |
+--------+--------------------------------------------------------------------+


# Showcase

## Data Preparation

Here is a fictious dataset.

```{r}
data = data.frame(x=c('Collection 1', 'Collection 2', 'Intersection'), 
                  y=c(40,50,20))
knitr::kable(data)
```

## Basic Venn

```{r}
echartr(data, x, y, type='venn') %>% 
    setTitle('Venn', 'Fictious Data')
```


# Futher Setup

Then you can configure the widgets, add markLines and/or markPoints, fortify the chart.

You can refer to related functions to play around on your own.

