---
title: "Basic Plots 04 - Candlestick"
author: "Yiying Wang"
date: "`r Sys.Date()`"
output: 
  knitr:::html_vignette:
    number_sections: yes
    toc: yes
    theme: cosmo
    self_contained: no
    lib_dir: libs
vignette: >
  %\VignetteIndexEntry{Basic Plots 04 - Candlestick}
  %\VignetteEngine{knitr::rmarkdown_notangle}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

First, you should load `rechartsX`:
```{r}
library(rechartsX)
```

# Introduction

Candlestick plot is also known as K chart:

<table id='intro'>
<tr><td>
```{r,echo=FALSE}
data(stock)
echartr(stock, as.character(date), c("open", "close", "low", "high"), type='k') %>% 
    setTheme('infographic', width=400, height=300) %>% 
    setTitle('Shanghai Stock Index 2013 1H') %>% setXAxis(name='Date') %>%
    setYAxis(name="Price")
```
</td>
<td>
</table>

The keys are:

- character `x` 
- numeric 'y' (four columns) aranged in the order of 'open', 'close', 'low', 'high'

# Function Call

```r
echartr(data, x, y, <t>, <type>)
```

+--------+--------------------------------------------------------------------+
| Arg    |  Requirement                                                       |
+========+====================================================================+
| **data** | source data in the form of data.frame                            |
+--------+--------------------------------------------------------------------+
| **x**  | character independent variable. Only the first one is accepted if multiple variables are provided. |
+--------+--------------------------------------------------------------------+
| **y**  | numeric dependent variable. Only the first four ones are accepted which are arranged in the order of 'open', 'close', 'low', 'high'. |
+--------+--------------------------------------------------------------------+
|  t     | timeline variable which will be coerced to factors. Only the first one is accepted if multiple variables are provided. |
+--------+--------------------------------------------------------------------+
| type   | 'k' or 'candlestick' |
+--------+--------------------------------------------------------------------+


# Showcase

## Basic Plot

```{r}
echartr(stock, as.character(date), c(open, close, low, high), type='k') %>%
    setXAxis(name='Date', axisLabel=list(rotate=30)) %>%
    setYAxis(name="Price")
```

## With Timeline

Remember the special notes in the [quick start](index.html)? We need to supplement the dataset to cover all the `x` and `t` levels.

```{r}
stock$Month <- format(stock$date, '%m')
stock$Day <- format(stock$date, '%d')
fullData <- data.frame(expand.grid(unique(stock$Month), unique(stock$Day)))
names(fullData) <- c("Month", "Day")
stock <- merge(stock, fullData, all.y=TRUE)
```

Then timeline will work properly.
```{r}
echartr(stock, Day, c(open, close, low, high), t=Month, type='k') %>%
    setYAxis(name="Price")
```

# Futher Setup

Then you can configure the widgets, add markLines and/or markPoints, fortify the chart.

You can refer to related functions to play around on your own.

