---
title: "Basic Plots 03 - Line/Area"
author: "Yiying Wang"
date: "`r Sys.Date()`"
output: 
  knitr:::html_vignette:
    number_sections: yes
    toc: yes
    theme: cosmo
    self_contained: no
    lib_dir: libs
vignette: >
  %\VignetteIndexEntry{Basic Plots 03 - Line/Area}
  %\VignetteEngine{knitr::rmarkdown_notangle}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

First, you should load `recharts`:
```{r}
library(recharts)
```

# Introduction

Line plot includes 4 basic types:

- line: line
- curve (smooth line): curve
- area: area
- wave (smooth area): wave

<table id='intro'>
<tr><td>
```{r,echo=FALSE}
titanic <- data.table::melt(apply(Titanic, c(1,4), sum))
names(titanic) <- c('Class', 'Survived', 'Count')
echartr(titanic, Class, Count, Survived, type='line') %>% setLegend(pos=3) %>%
    setTheme('infographic', width=400, height=300) %>%
    setTitle('Titanic: Survival by Cabin Class','line')
```
</td>
<td>
```{r,echo=FALSE}
echartr(titanic, Class, Count, Survived, type='curve') %>% 
    setTheme('roma', width=400, height=300) %>% setLegend(pos=3) %>%
    setTitle('Titanic: Outcome by Cabin Class','curve')
```
</td></tr>
<tr><td>
```{r,echo=FALSE}
echartr(titanic, Class, Count, Survived, type='area') %>% setLegend(pos=3) %>%
    setTheme('macarons', width=400, height=300) %>%
    setTitle('Titanic: Survival by Cabin Class','area')
```
</td>
<td>
```{r,echo=FALSE}
echartr(titanic, Class, Count, Survived, type='wave') %>% 
    setTheme('macarons2', width=400, height=300) %>% setLegend(pos=3) %>%
    setTitle('Titanic: Outcome by Cabin Class','wave')
```
</td></tr>
</table>

The keys are:

- character `x` and numeric `y`
- each combination level of `x` (and `series`) can only have one `y` data point
- Tiled and stacked bar/column charts can shift from one to another by clicking type shift buttons in the toolbox widget.
- Line/area can shift to bar charts easily using buttons in toolbox widget.

# Function Call

```r
echartr(data, x, y, <series>, <weight>, <t>, <type>, <subtype>)
```

+---------+--------------------------------------------------------------------+
| Arg     |  Requirement                                                       |
+=========+====================================================================+
| **data**| source data in the form of data.frame                            |
+---------+--------------------------------------------------------------------+
| **x**   | character independent variable. Other type will be coerced to factors. Only the first one is accepted if multiple variables are provided. |
+---------+--------------------------------------------------------------------+
| **y**   | numeric dependent variable. Only the first one is accepted if multiple variables are provided. |
+---------+--------------------------------------------------------------------+
| series  | data series variable which will be coerced to factors. Only the first one is accepted if multiple variables are provided. |
+---------+--------------------------------------------------------------------+
| weight  | weight is mapped to the lineWidth of the chart by series |
+---------+--------------------------------------------------------------------+
|  t      | timeline variable which will be coerced to factors. Only the first one is accepted if multiple variables are provided. |
+---------+--------------------------------------------------------------------+
| type    | 'line', 'curve', 'area', 'wave' |
+---------+--------------------------------------------------------------------+
| subtype | - line: c("stack","smooth","dotted","solid","dashed") | 
|         |      + stack: stacked series |
|         |      + smooth: smooth line |
|         |      + dotted: use dotted line |
|         |      + solid: use solid line (default) |
|         |      + dashed: use dashed line |
|         | - curve: c("stack","solid") |
|         | - area: c("stack","smooth","dotted","solid","dashed")  |
|         | - wave: c("stack","solid") |
+---------+--------------------------------------------------------------------+

# Showcase

## Data Preparation

Let's look into `airquality` dataset embeded in the package `datasets`. The structure of the data.frame is as below:

```{r}
aq <- airquality
aq$Date <- as.Date(paste('1973', aq$Month, aq$Day, sep='-'))
aq$Day <- as.character(aq$Day)
aq$Month <- factor(aq$Month, labels=c("May", "Jun", "Jul", "Aug", "Sep"))
head(aq)
```

## Line Chart

### Singular Series

`type` is set 'line'.

```{r}
echartr(aq, Date, Temp, type='line') %>%
    setTitle('NY Temperature May - Sep 1973') %>% setSymbols('none')
```

### Multiple Series

```{r}
echartr(aq, Day, Temp, Month, type='line') %>%
    setTitle('NY Temperature May - Sep 1973, by Month') %>% 
    setSymbols('emptycircle')
```

### Stacked Line Chart

Set `type` 'line' and `subtype` 'stack'.

```{r}
echartr(aq, Day, Temp, Month, type='line', subtype='stack') %>%
    setTitle('NY Temperature May - Sep 1973, by Month') %>% 
    setSymbols('emptycircle')
```

### Line Width Mapped to `Weight`

Let the lineWidth linked to the mean of Wind across series (Month).

```{r}
echartr(aq, Day, Temp, Month, weight=Wind, type='line') %>%
    setTitle('NY Temperature May - Sep 1973, by Month') %>% 
    setSymbols('emptycircle')
```

### Line Chart with Timeline

```{r}
echartr(aq, Day, Temp, t=Month, type='line') %>%
    setTitle('NY Temperature May - Sep 1973, by Month') %>% 
    setSymbols('emptycircle')
```

## Curve (Smooth Line) Chart

### Tiled Smooth Line Chart

Set `type` 'curve'.

```{r}
echartr(aq, Day, Temp, Month, type='curve') %>%
    setTitle('NY Temperature May - Sep 1973, by Month') %>% 
    setSymbols('emptycircle')
```

### Stacked Smooth Line Chart

Set `type` 'curve' and `subtype` 'stack'.

```{r}
echartr(aq, Day, Temp, Month, type='curve', subtype='stack') %>%
    setTitle('NY Temperature May - Sep 1973, by Month') %>% 
    setSymbols('emptycircle')
```

## Area Chart

### Tiled Area Chart

Area chart is exactly the same with line chart except that it has `areaStyle` feature specialized.

Set `type` 'area'.

```{r}
echartr(aq, Date, Temp, type='area') %>%
    setTitle('NY Temperature May - Sep 1973') %>% 
    setSymbols('emptycircle')
```

### Stacked Area Chart

Set `type` 'area' and `subtype` 'stack'.

```{r}
echartr(aq, Day, Temp, Month, type='area', subtype='stack') %>%
    setTitle('NY Temperature May - Sep 1973, by Month') %>% 
    setSymbols('emptycircle')
```

## Wave (Smooth Area) Chart

### Tiled Smooth Area Chart

Set `type` 'wave'.

```{r}
echartr(aq, Date, Temp, type='wave') %>%
    setTitle('NY Temperature May - Sep 1973') %>% 
    setSymbols('emptycircle')
```

### Stacked Smooth Area Chart

Set `type` 'wave' and `subtype` 'stack'.

```{r}
echartr(aq, Day, Temp, Month, type='wave', subtype='stack') %>%
    setTitle('NY Temperature May - Sep 1973, by Month') %>% 
    setSymbols('emptycircle')
```

# Futher Setup

Then you can configure the widgets, add markLines and/or markPoints, fortify the chart.

You can refer to related functions to play around on your own.

