---
title: "Widget 21 - Title"
author: "Yiying Wang"
date: "`r Sys.Date()`"
output: 
  knitr:::html_vignette:
    number_sections: yes
    theme: cosmo
    toc: yes
    self_contained: no
    lib_dir: libs
vignette: >
  %\VignetteIndexEntry{Widget 21 - Title}
  %\VignetteEngine{knitr::rmarkdown_notangle}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

First, you should load `rechartsX`:
```{r}
library(rechartsX)
```

# Introduction

Title comprises of two parts: title (and title link), subtitle (and subtitle link). The default position is 6 o'clock.

The recommended approach to use `setTitle` is `chart %>% setTitle(...)`.

# Function Call

```r
setTitle(chart, title = NULL, subtitle = NULL, link = NULL,
  sublink = NULL, pos = 6, bgColor = NULL, borderColor = NULL,
  borderWidth = NULL, textStyle = NULL, subtextStyle = NULL,
  show = TRUE, ...)
```

+-------------+----------------------------------------------------------------+
|   Arg       |  Requirement                                                |
+=============+================================================================+
| **chart**   | Echarts object generated by `echartR` or `echart`.  |
+-------------+----------------------------------------------------------------+
| title       | text of the title. If written in markdown format `[caption](url)`, then caption is passed to title, url is passed to link. If the length of the title vector equals to the length of timeline slices, the title vector will be used as slice-specific user-defined title. |
+-------------+----------------------------------------------------------------+
| subtitle    | text of the subtitle. If written in markdown format `[caption](url)`, then caption is passed to subtitle, url is passed to sublink. If the length of the subtitle vector equals to the length of timeline slices, the subtitle vector will be used as slice-specific user-defined title. |
+-------------+----------------------------------------------------------------+
| link        | link of the title |
+-------------+----------------------------------------------------------------+
| sublink     | link of the subtitle |
+-------------+----------------------------------------------------------------+
| pos         | the clock-position of title (and subtitle), refer to `vecPos`. Or define a vector `c(x, y, orient)` yourself. |
+-------------+----------------------------------------------------------------+
| bgColor     | background color of title. Default 'rgba(0,0,0,0)' (transparent) |
+-------------+----------------------------------------------------------------+
| borderColor | border color of the title. Default '#ccc'. |
+-------------+----------------------------------------------------------------+
| borderWidth | border width of the title. Default 0px (not shown). |
+-------------+----------------------------------------------------------------+
| textStyle   | You can place self-defined textStyle list of the title here. E.g., `list(fontFamily='Arial|Verdana|sans-serif'`, `fontSize=20,` `fontWeight='normal|bold|bolder|lighter|<numbers>',` `fontStyle='normal|italic|oblique', color='red')` |
+-------------+----------------------------------------------------------------+
| subtextStyle| You can place self-defined textStyle of the subtitle here. |
+-------------+----------------------------------------------------------------+
| show        | Logical. Whether to show the title. If you want to remove title from the echarts object, set it NULL. |
+-------------+----------------------------------------------------------------+
| ...         | Elipsis. |
+-------------+----------------------------------------------------------------+

# Showcase

```{r}
g1 <- echartr(iris, Sepal.Width, Petal.Width, Species)
g2 <- echartr(iris, Sepal.Width, Petal.Width, t=Species)
```

<table>
<tr><td>
```{r}
g1 %>% setTheme(width=400, height=300)
```
</td><td>
```{r}
g2 %>% setTheme(width=400, height=300)
```
</td></tr>
</table>

## Echarts without Timeline

Title and subtitle at the default position.
```{r}
g1 %>% setTitle(title='Iris data set', subtitle='by: R. A. Fisher')
```

Relocate the title.
```{r}
g1 %>% setTitle(title='Iris data set', subtitle='by: R. A. Fisher', pos=12)
```

Title and subtitle with links.
```{r}
g1 %>% setTitle(
  '[Iris data set](https://en.wikipedia.org/wiki/Iris_flower_data_set)',
  '[R. A. Fisher](https://en.wikipedia.org/wiki/Ronald_Fisher)')
```

Customize the format (ugly).
```{r}
g1 %>% setTitle(
  '[Iris data set](https://en.wikipedia.org/wiki/Iris_flower_data_set)',
  '[R. A. Fisher](https://en.wikipedia.org/wiki/Ronald_Fisher)',
  textStyle=textStyle(fontFamily='Courier New', fontSize=24, color='gold'),
  subtextStyle=textStyle(color='silver'), bgColor='lightgreen') %>%
    setGrid(y2=90)
```

## Echarts with Timeline

Title and subtitle at the default position.
```{r}
g2 %>% setTitle(
    '[Iris data set](https://en.wikipedia.org/wiki/Iris_flower_data_set)',
    '[R. A. Fisher](https://en.wikipedia.org/wiki/Ronald_Fisher)')
```

Customierzed titles and subtitles. They must be written in vectors and will be then mapped to each timeslots along with the timeline.
```{r}
titles <- c(
    '[Iris setosa](https://en.wikipedia.org/wiki/Iris_setosa)',
    '[Iris versicolor](https://en.wikipedia.org/wiki/Iris_versicolor)',
    '[Iris virginica](https://en.wikipedia.org/wiki/Iris_virginica)')
g2 %>% setTitle(titles)
```

More settings on format. Elements such as textStyle should also be written in lists to map to each timeslots.
```{r}
g2 %>% setTitle(
    titles,
    textStyle=list(
      textStyle(fontFamily='Impact', color='red', fontStyle='normal'),
      textStyle(fontFamily='Times New Roman', color='darkgreen'),
      textStyle(fontFamily='Calibri', color='blue', fontStyle='oblique')
   ),
   bgColor='yellow')
```

# References

<http://echarts.baidu.com/echarts2/doc/option.html#title~title>
